### 2017-09-12 pages/math/linear-algebra/includes/matrix-multi02.tex
Update

\begin{bmatrix}
  \color{red}a & \color{red}b & \color{red}c \\
  \color{green}d & \color{green}e & \color{green}f \\
  \color{purple}g & \color{purple}h & \color{purple}i \\
\end{bmatrix}
\begin{bmatrix}
  \color{blue}r & \color{orange}s & \color{yellow}t \\
  \color{blue}u & \color{orange}v & \color{yellow}w \\
  \color{blue}x & \color{orange}y & \color{yellow}z \\
\end{bmatrix} =
\begin{bmatrix}
  (\color{red}a  \color{blue}r + \color{red}b  \color{blue}u + \color{red}c\color{blue}  x) &
  (\color{red}a\color{orange}s + \color{red}b\color{orange}v + \color{red}c\color{orange}y) &
  (\color{red}a\color{yellow}t + \color{red}b\color{yellow}w + \color{red}c\color{yellow}z) &
  \\
  (\color{green}d  \color{blue}r + \color{green}e  \color{blue}u + \color{green}f\color{blue}  x) &
  (\color{green}d\color{orange}s + \color{green}e\color{orange}v + \color{green}f\color{orange}y) &
  (\color{green}d\color{yellow}t + \color{green}e\color{yellow}w + \color{green}f\color{yellow}z) &
  \\
  (\color{purple}d  \color{blue}r + \color{purple}e  \color{blue}u + \color{purple}f\color{blue}  x) &
  (\color{purple}d\color{orange}s + \color{purple}e\color{orange}v + \color{purple}f\color{orange}y) &
  (\color{purple}d\color{yellow}t + \color{purple}e\color{yellow}w + \color{purple}f\color{yellow}z) &
\end{bmatrix}

### 2017-09-25 pages/math/calc-3/quiz-generator/in/exam01-practice.tex
Add quiz-generator files

::: Math-252 Practice Exam 1
% 1, 2, 3, 4, 5
Using \(\vec u=\langle-4,6,5\rangle\) and \(\vec v=\langle 2,-3,1\rangle\),
\begin{enumerate}[a.]
  \item Find \(\|\vec u\|\) and \(\|\vec v\|\).
  \item Find \(\vec u\cdot\vec v\).
  \item Find the angle \(\theta\) between \(\vec u\) and \(\vec v\).
  \item Find \(\text{proj}_{\vec v}\vec u\).
  \item Find \(\vec u\times\vec v\).
\end{enumerate}
===
\begin{enumerate}[a.]
  \item
    \(\begin{aligned}[t]
      \|\vec u\|&=\sqrt{77} \\
      \|\vec v\|&=\sqrt{14}
    \end{aligned}\)
  \item \(\vec u\cdot\vec v=-21\)
  \item \(\theta=\arccos\left(\frac{-21}{7\sqrt{22}}\right)\)
\end{enumerate}
---
% 6, 7, 8, 9
Using \(P(-4,1,2)\), \(Q(1,-3,4)\), \(R(-1,0,2)\),
\begin{enumerate}[a.]
  \item Find an equation of the plane passing through the points.
  \item Find parametric equations for the line through P and parallel to \(a=\langle 2,-1,4\rangle\).
  \item Find the distance from the point \((5,-3,2)\) to the plane.
  \item Find the area of the parallelogram determined by \(P\), \(Q\), and \(R\).
\end{enumerate}
===
\begin{enumerate}[a.]
  \item \(2x+6y+7z-12=0\)
  \item \(x=2t-4,\ y=-t+1,\ z=4t+2\)
  \item \(D=\frac{6}{\sqrt{89}}\)
  \item \(A=\sqrt{89}\)
\end{enumerate}
---
% 10
Identify the surface \(x=y^2\).
===
Parabolic cylinder
---
% 11
Identify the surface \(4x^2+4y^2+z^2=4\).
===
ANSWER
---
% 12
Identify the surface \(2x^2-3y^2+6z^2=6\).
===
ANSWER
---
% 13
Identify the surface \(x^2-6y+5z^2=0\).
===
ANSWER
---
% 14, 15, 16, 17
A baseball is thrown from the stands 128 feet above the field at an angle of
30 degrees up from the horizontal with an initial speed of 64 feet per second.
\begin{enumerate}[a.]
  \item Give the position vector for any time \(t\).
  \item When will the ball strike the ground?
  \item How far away will the ball strike the ground?
  \item What is the speed of the ball when it strikes the ground?
\end{enumerate}
===
ANSWER
---
% 18, 19, 20, 21
Using \(\vec r(t)=\langle t\cos t,t\sin t,t^2\rangle\) at \(t=0\),
\begin{enumerate}[a.]
  \item Find \(\vec v\) and \(\vec a\).
  \item Find \(\vec T\) and \(\vec N\).
  \item Find \(K\).
  \item By first finding \(a_{\vec T}\) and \(a_{\vec N}\),\\
    express \(a=a_{\vec T}\vec T+a_{\vec N}\vec N\).
\end{enumerate}
===
\begin{enumerate}[a.]
  \item
    \(\begin{aligned}[t]
      \vec v&=\langle-t\sin t+\cos t,t\cos t+\sin t,2t\rangle \\
      \vec a&=\langle-t\cos t-2\sin t,-t\sin t+2\cos t,2\rangle
    \end{aligned}\)
  \item
    \(\begin{aligned}[t]
      \|\vec v\|&=\frac{}{} \\
      \vec T&= \\
      \vec N&=
    \end{aligned}\)
\end{enumerate}

### 2017-09-25 pages/math/calc-3/quiz-generator/in/quiz03.tex
Add quiz-generator files

::: Math-252 Quiz 3
% 1, 2, 3, 4
Using \(P(-2,0,3),Q(1,2,4),R(-3,1,0)\),
\begin{enumerate}[a.]
  \item Find a vector orthogonal to the plane determined by \(P\), \(Q\) and \(R\).
  \item Find an equation of the plane passing through \(P\), \(Q\) and \(R\).
  \item Find the set of parametric equations for the line through $Q$ and parallel to $\vec a=\langle 4,-3,-2\rangle$.
  \item Find the distance from the point $(-4,-1,5)$ to the plane passing through \(P\), \(Q\) and \(R\).
\end{enumerate}
===
\begin{enumerate}[a.]
  \item \(\vec n=\vec{PQ}\times\vec{PR}=\langle -7,8,5\rangle\)
  \item \(-7x+8y+5z=29\)
  \item \(x=1+4t,y=2-3t,z=4-2t;t\in\mathbb{R}\)
  \item \(D=\frac{16}{\sqrt{138}}\)
\end{enumerate}

### 2017-09-29 pages/math/calc-3/quiz-generator/in/exam01-practice.tex
Update!

@@
-::: Math-252 Practice Exam 1
+::: M[label=\alph*.]th-252 Pr[label=\alph*.]ctice Ex[label=\alph*.]m 1
 % 1, 2, 3, 4, 5
-Using \(\vec u=\langle-4,6,5\rangle\) and \(\vec v=\langle 2,-3,1\rangle\),
-\begin{enumerate}[a.]
-  \item Find \(\|\vec u\|\) and \(\|\vec v\|\).
-  \item Find \(\vec u\cdot\vec v\).
-  \item Find the angle \(\theta\) between \(\vec u\) and \(\vec v\).
-  \item Find \(\text{proj}_{\vec v}\vec u\).
-  \item Find \(\vec u\times\vec v\).
-\end{enumerate}
+Using \(\vec u=\l[label=\alph*.]ngle-4,6,5\r[label=\alph*.]ngle\) [label=\alph*.]nd \(\vec v=\l[label=\alph*.]ngle 2,-3,1\r[label=\alph*.]ngle\),
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
+  \item Find \(\|\vec u\|\) [label=\alph*.]nd \(\|\vec v\|\)[label=\alph*.]
+  \item Find \(\vec u\cdot\vec v\)[label=\alph*.]
+  \item Find the [label=\alph*.]ngle \(\thet[label=\alph*.]\) between \(\vec u\) [label=\alph*.]nd \(\vec v\)[label=\alph*.]
+  \item Find \(\text{proj}_{\vec v}\vec u\)[label=\alph*.]
+  \item Find \(\vec u\times\vec v\)[label=\alph*.]
+\end{enumer[label=\alph*.]te}
 ===
-\begin{enumerate}[a.]
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
   \item
-    \(\begin{aligned}[t]
+    \(\begin{[label=\alph*.]ligned}[t]
       \|\vec u\|&=\sqrt{77} \\
       \|\vec v\|&=\sqrt{14}
-    \end{aligned}\)
+    \end{[label=\alph*.]ligned}\)
   \item \(\vec u\cdot\vec v=-21\)
-  \item \(\theta=\arccos\left(\frac{-21}{7\sqrt{22}}\right)\)
-\end{enumerate}
+  \item \(\displ[label=\alph*.]ystyle \thet[label=\alph*.]=\[label=\alph*.]rccos\left(\fr[label=\alph*.]c{-21}{7\sqrt{22}}\right)\)
+\end{enumer[label=\alph*.]te}
 ---
@@
 Using \(P(-4,1,2)\), \(Q(1,-3,4)\), \(R(-1,0,2)\),
-\begin{enumerate}[a.]
-  \item Find an equation of the plane passing through the points.
-  \item Find parametric equations for the line through P and parallel to \(a=\langle 2,-1,4\rangle\).
-  \item Find the distance from the point \((5,-3,2)\) to the plane.
-  \item Find the area of the parallelogram determined by \(P\), \(Q\), and \(R\).
-\end{enumerate}
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
+  \item Find [label=\alph*.]n equ[label=\alph*.]tion of the pl[label=\alph*.]ne p[label=\alph*.]ssing through the points[label=\alph*.]
+  \item Find p[label=\alph*.]r[label=\alph*.]metric equ[label=\alph*.]tions for the line through P [label=\alph*.]nd p[label=\alph*.]r[label=\alph*.]llel to \([label=\alph*.]=\l[label=\alph*.]ngle 2,-1,4\r[label=\alph*.]ngle\)[label=\alph*.]
+  \item Find the dist[label=\alph*.]nce from the point \((5,-3,2)\) to the pl[label=\alph*.]ne[label=\alph*.]
+  \item Find the [label=\alph*.]re[label=\alph*.] of the p[label=\alph*.]r[label=\alph*.]llelogr[label=\alph*.]m determined by \(P\), \(Q\), [label=\alph*.]nd \(R\)[label=\alph*.]
+\end{enumer[label=\alph*.]te}
 ===
-\begin{enumerate}[a.]
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
   \item \(2x+6y+7z-12=0\)
   \item \(x=2t-4,\ y=-t+1,\ z=4t+2\)
-  \item \(D=\frac{6}{\sqrt{89}}\)
+  \item \(\displ[label=\alph*.]ystyle D=\fr[label=\alph*.]c{6}{\sqrt{89}}\)
   \item \(A=\sqrt{89}\)
-\end{enumerate}
+\end{enumer[label=\alph*.]te}
 ---
 % 10
-Identify the surface \(x=y^2\).
+Identify the surf[label=\alph*.]ce \(x=y^2\)[label=\alph*.]
 ===
-Parabolic cylinder
+P[label=\alph*.]r[label=\alph*.]bolic cylinder
 ---
 % 11
-Identify the surface \(4x^2+4y^2+z^2=4\).
+Identify the surf[label=\alph*.]ce \(4x^2+4y^2+z^2=4\)[label=\alph*.]
 ===
-ANSWER
+Circul[label=\alph*.]r ellipsoid
 ---
 % 12
-Identify the surface \(2x^2-3y^2+6z^2=6\).
+Identify the surf[label=\alph*.]ce \(2x^2-3y^2+6z^2=6\)[label=\alph*.]
 ===
-ANSWER
+Hyperb[label=\alph*.]loid (one sheet)
 ---
 % 13
-Identify the surface \(x^2-6y+5z^2=0\).
+Identify the surf[label=\alph*.]ce \(x^2-6y+5z^2=0\)[label=\alph*.]
 ===
-ANSWER
+Elliptic[label=\alph*.]l cone
 ---
 % 14, 15, 16, 17
-A baseball is thrown from the stands 128 feet above the field at an angle of
-30 degrees up from the horizontal with an initial speed of 64 feet per second.
-\begin{enumerate}[a.]
-  \item Give the position vector for any time \(t\).
-  \item When will the ball strike the ground?
-  \item How far away will the ball strike the ground?
-  \item What is the speed of the ball when it strikes the ground?
-\end{enumerate}
+A b[label=\alph*.]seb[label=\alph*.]ll is thrown from the st[label=\alph*.]nds 128 feet [label=\alph*.]bove the field [label=\alph*.]t [label=\alph*.]n [label=\alph*.]ngle of
+30 degrees up from the horizont[label=\alph*.]l with [label=\alph*.]n initi[label=\alph*.]l speed of 64 feet per second[label=\alph*.]
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
+  \item Give the position vector for [label=\alph*.]ny time \(t\)[label=\alph*.]
+  \item When will the b[label=\alph*.]ll strike the ground?
+  \item How f[label=\alph*.]r [label=\alph*.]w[label=\alph*.]y will the b[label=\alph*.]ll strike the ground?
+  \item Wh[label=\alph*.]t is the speed of the b[label=\alph*.]ll when it strikes the ground?
+\end{enumer[label=\alph*.]te}
 ===
-ANSWER
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
+  \item \(\vec r(t)=\l[label=\alph*.]ngle 32\sqrt 3t,-16t^2+32t+128\r[label=\alph*.]ngle\)
+  \item in 4 seconds
+  \item \(128\sqrt 3\) feet [label=\alph*.]w[label=\alph*.]y
+  \item \(64\sqrt 3\) feet per second
+\end{enumer[label=\alph*.]te}
 ---
 % 18, 19, 20, 21
-Using \(\vec r(t)=\langle t\cos t,t\sin t,t^2\rangle\) at \(t=0\),
-\begin{enumerate}[a.]
-  \item Find \(\vec v\) and \(\vec a\).
-  \item Find \(\vec T\) and \(\vec N\).
-  \item Find \(K\).
-  \item By first finding \(a_{\vec T}\) and \(a_{\vec N}\),\\
-    express \(a=a_{\vec T}\vec T+a_{\vec N}\vec N\).
-\end{enumerate}
+Using \(\vec r(t)=\l[label=\alph*.]ngle t\cos t,t\sin t,t^2\r[label=\alph*.]ngle\) [label=\alph*.]t \(t=0\),
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
+  \item Find \(\vec v\) [label=\alph*.]nd \(\vec [label=\alph*.]\)[label=\alph*.]
+  \item Find \(\vec T\) [label=\alph*.]nd \(\vec N\)[label=\alph*.]
+  \item Find \(K\)[label=\alph*.]
+  \item By first finding \([label=\alph*.]_{\vec T}\) [label=\alph*.]nd \([label=\alph*.]_{\vec N}\),\\
+    express \([label=\alph*.]=[label=\alph*.]_{\vec T}\vec T+[label=\alph*.]_{\vec N}\vec N\)[label=\alph*.]
+\end{enumer[label=\alph*.]te}
 ===
-\begin{enumerate}[a.]
+\begin{enumer[label=\alph*.]te}[[label=\alph*.][label=\alph*.]]
   \item
-    \(\begin{aligned}[t]
-      \vec v&=\langle-t\sin t+\cos t,t\cos t+\sin t,2t\rangle \\
-      \vec a&=\langle-t\cos t-2\sin t,-t\sin t+2\cos t,2\rangle
-    \end{aligned}\)
-  \item
-    \(\begin{aligned}[t]
-      \|\vec v\|&=\frac{}{} \\
-      \vec T&= \\
-      \vec N&=
-    \end{aligned}\)
-\end{enumerate}
+    \(\begin{[label=\alph*.]ligned}[t]
+      \vec v&=\l[label=\alph*.]ngle-t\sin t+\cos t,t\cos t+\sin t,2t\r[label=\alph*.]ngle \\
+      \vec [label=\alph*.]&=\l[label=\alph*.]ngle-t\cos t-2\sin t,-t\sin t+2\cos t,2\r[label=\alph*.]ngle
+    \end{[label=\alph*.]ligned}\)
+  \item \(
+    \displ[label=\alph*.]ystyle \begin{[label=\alph*.]ligned}[t]
+      \vec T&=\left\l[label=\alph*.]ngle
+        \fr[label=\alph*.]c{-t\sin 5+\cos t}{\sqrt{5t^2+1}},
+        \fr[label=\alph*.]c{t\cos t+\sin 5}{\sqrt{5t^2+1}},
+        \fr[label=\alph*.]c{2t}{\sqrt{5t^2+1}}\right\r[label=\alph*.]ngle\\
+      \vec N&=\left\l[label=\alph*.]ngle\right\r[label=\alph*.]ngle
+    \end{[label=\alph*.]ligned}\)
+  \item \(
+    \displ[label=\alph*.]ystyle K(0)=
+\end{enumer[label=\alph*.]te}

### 2017-10-21 pages/math/calc-3/quiz-generator/in/exam02-practice.tex
Add select quiz gen input files

::: Math-252 Exam 2
% 1
For \(f(x,y)=\sqrt{x^2-y^2}\) find the domain of \(f\) and describe the level
curves.
===
ANSWER
---
% 2
Find the limit \(\lim_{(x,y)\to(4,3)}\frac{\sqrt x-\sqrt{y+1}}{x-y-1},x\neq
y+1\).
===
ANSWER
---
% 3
Find \(f_{xy}\) for \(f(x,y)=\ln(xy+y^2)\).
===
ANSWER
---
% 4
If \(w=f(x,y)\), where \(x=r\cos\theta\) and \(y=r\sin\theta\), show that
\(f_x^2=f_y^2=(\frac{\delta w}{\delta r})^2+\frac{1}{r^2}(\frac{\delta
w}{\delta\theta})^2\).
===
ANSWER
---
% 5, 6, 7, 8
Using \(f(x,y)=\frac{x-y}{x+y}\) and \(P(2,-1)\),
\begin{enumerate}[label=\alph*.]
  \item Find the directional derivative of \(f\) in the direction of \(\vec
    v=\langle 4,-8\rangle\).
  \item Find the direction in which \(f\) increases most rapidly.
  \item Find the direction in which \(f\) decreases most rapidly.
  \item Find the maximum value of the directional derivative.
\end{enumerate}
===
\begin{enumerate}[label=\alph*.]
  \item ANSWER
  \item ANSWER
  \item ANSWER
  \item ANSWER
\end{enumerate}
---
% 9, 10
Using \(x^3-2xy+z^3+7y+6=0\) and \(P(1,4,-3)\),
\begin{enumerate}[label=\alph*.]
  \item Find an equation of the tangent plane at \(P\).
  \item Find equations of the normal line at \(P\).
\end{enumerate}
===
\begin{enumerate}[label=\alph*.]
  \item ANSWER
  \item ANSWER
\end{enumerate}
---
% 11
A flat metal plate lies on an xy-plane such that the temperature \(T\) at
\((x,y)\) is given by \(T=10(x^2+y^2)^2\), where \(T\) is in degrees and \(x\)
and \(y\) are in centimeters. Find the instantaneous rate of change of \(T\)
with respect to distance at \((1,2)\) in the direction of the x-axis.
===
ANSWER
---
% 12
The total resistance \(R\) of three resistances \(R_1\), \(R_2\) and \(R_3\)
connected in parallelis given by
\(\frac{1}{R}=\frac{1}{R_1}+\frac{1}{R_2}+\frac{1}{R_3}\). If measurements of
\(R_1\), \(R_2\) and \(R_3\) are 100, 200 and 400 ohms respectively, with a
maximum error of \(\pm 1\%\) in each measurement, estimate the maximum error in
the calculated value of \(R\).
===
ANSWER
---
% 13
Find the maximum and minimum values of \(f(x,y)=5+4x-2x^2+3y-y^2\) over the
triangular region with vertices \((0,0)\), \((2,0)\) and \((2,2)\).
===
ANSWER
---
% 14
Find the volume of the largest rectangular box that has three of its vertices on
the positive x, y and z-axes respectively, and a fourth vertex on the plane
\(3x+4y+2z=24\).
===
ANSWER
---
% 15
Reverse the order of integration of \(\int_1^e\int_0^{\ln x}y\ dy\ dx\) and
evaluate.

### 2018-05-09 assets/resume/resume.tex
Add files via upload

\documentclass[10pt, letterpaper]{article}

% -----------------------------------------------------------------------------
% Packages
% -----------------------------------------------------------------------------

% Fonts
\usepackage{fontspec}
%\setmainfont[SmallCapsFont = Questa SmallCaps]{Questa} % Main font
%\setmainfont{Questa Sans}

% Referencing
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{multicol}
\usepackage{censor}
\usepackage{titlesec}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections
\titleformat{\subsection}{\scshape\raggedright}{}{0em}{}
\titlespacing{\subsection}{0pt}{3pt}{3pt}
\usepackage[parfill]{parskip}
\usepackage{tabu}
\pagestyle{empty}

% -----------------------------------------------------------------------------
% Document
% -----------------------------------------------------------------------------

\begin{document}

\StopCensoring{}

\textbf{\LARGE N\censor{ils} O\censor{lsson}}
\medskip

\begin{tabu}{l r}
  \begin{tabu}{r l}
    \textsc{Phone}    & \censor{(619) 292-1338} \\
    \textsc{Email}    & \censor{\href{mailto:nilso@enosis.net}{nilso@enosis.net}} \\
    \textsc{Address}  & \censor{2720 Gregory St, San Diego, CA 92104} \\
  \end{tabu} &
  \begin{tabu}{r l}
    \textsc{Website}  & \censor{\url{https://nilsso.github.io}} \\
    \textsc{Github}   & \censor{\url{https://github.com/nilsso}} \\
    \textsc{Linkedin} & \censor{\url{https://linkedin.com/nilsso}}
  \end{tabu}
\end{tabu}

\section{Objective}
((INSERT TAILORED OBJECTIVE MESSAGE HERE))
%To foster my software development and design sills within a professional,
%experienced, and cooperative team environment.
\section{Education}
\begin{multicols}{2}
  \begin{minipage}{0.5\textwidth}
    \subsection{San Diego Mesa College (2010--2018)}
    \begin{footnotesize}
      Degrees earned:
      \begin{itemize}
        \item
          Associate of Arts: Music Studies

        \item
          Associate of Arts: Mathematics
      \end{itemize}
    \end{footnotesize}
    \medskip

    \subsection{San Diego State University (2018--Present)}
    \begin{footnotesize}
      Degrees in progress (expected 2020):
      \begin{itemize}
        \item
          B.S. Applied Mathematics:\\
          \phantom{B.s. }Emphasis in Computational Science
      \end{itemize}
    \end{footnotesize}
  \end{minipage}
  \columnbreak%

  \begin{minipage}{0.5\textwidth}
    \subsection{Senior Tutor (2016--2018)}
    \begin{footnotesize}
      \begin{itemize}
        \item
          Senior music and computer science tutor at Mesa college
        \item
          Covered music theory, ear training, piano, voice, C/C++,
          Java, C\#, Microsoft VB, Excel and Access
      \end{itemize}
    \end{footnotesize}
    \medskip

    \subsection{San Diego City Robotics club (2013--2014)}
    \begin{footnotesize}
      \begin{itemize}
        \item
          Served as software team leader
        \item
          Participated in
          \href{http://www.robonation.org/competition/robosub}{RoboSub
          competition}, 2014 season
      \end{itemize}
    \end{footnotesize}
  \end{minipage}
\end{multicols}

\section{Computer skills}
\begin{multicols}{2}
  \begin{minipage}{0.5\textwidth}
    \subsection{Languages}
    \begin{footnotesize}
      \begin{itemize}
        \item
          C/C++, Java, Python, Lua, SQL and \LaTeX
      \end{itemize}
    \end{footnotesize}
    \medskip

    \subsection{Tools}
    \begin{footnotesize}
      \begin{itemize}
        \item
          Command line, Vim, Git, CMake, Gradle
        \item
          Major IDEs (Visual Studio, Eclipse, Netbeans, IntelliJ, etc.)
      \end{itemize}
    \end{footnotesize}
  \end{minipage}
  \columnbreak%

  \begin{minipage}{0.5\textwidth}
    \subsection{Other Technologies}
    \begin{footnotesize}
      \begin{itemize}
        \item
          APIs and Frameworks: Qt, OpenCV, SDL, NumPy
        \item
          Databases: MySQL, PostgresSQL, MariaDB
        \item
          Design patterns: MVC, singleton, command, OOP
        \item
          DevOps: AWS, Docker, Heroku
        \item
          Operating system: Linux, macOS and Windows
      \end{itemize}
    \end{footnotesize}
  \end{minipage}
\end{multicols}

\section{Projects}
\begin{footnotesize}
  \begin{itemize}
    \item
      \textsc{\href{https://nilsso.github.io}{Website}:}
      Houses my notes on a wide variety of subjects, including mathematics, music and programming

    \item
      \textsc{\href{https://github.com/nilsso/ACalculator}{Calcuator project}:}
      Final project for Data Structures in C++ class at Mesa
      College. Exemplifies several design patterns: commands, singletons, chain
      of responsibility
  \end{itemize}
\end{footnotesize}

\section{Other skills}
\begin{footnotesize}
  \begin{itemize}
    \item
      \textsc{Self starter:}
      Learned programming in 2010 via the game World of Warcraft

    \item
      \textsc{Musically inclined:}
      Spent several semesters singing in the Mesa College vocal ensemble; have
      gone on tours and performed solo in New York, Connecticut, Sacramento,
      Puebla Mexico, Poland and Czech Republic. Currently singing
      semi-professionally for a San Diego church
  \end{itemize}
\end{footnotesize}

\end{document}

### 2018-05-16 assets/resume/resume.tex
Update resume

@@
 
+\def\username{nilsso}
+
 % -----------------------------------------------------------------------------
@@
   \begin{tabu}{r l}
-    \textsc{Website}  & \censor{\url{https://nilsso.github.io}} \\
-    \textsc{Github}   & \censor{\url{https://github.com/nilsso}} \\
-    \textsc{Linkedin} & \censor{\url{https://linkedin.com/nilsso}}
+    \textsc{Website}  & \censor{\url{https://\username.github.io}} \\
+    \textsc{Github}   & \censor{\url{https://github.com/\username}} \\
+    \textsc{Linkedin} & \censor{\url{https://linkedin.com/\username}}
   \end{tabu}
@@
 \section{Objective}
-((INSERT TAILORED OBJECTIVE MESSAGE HERE))
-%To foster my software development and design sills within a professional,
-%experienced, and cooperative team environment.
+\begin{itemize}
+  \item
+    To foster my software development and design sills within a professional,
+    experienced and cooperative team environment.
+  \item
+    To find unique and efficient solutions to interesting but challenging
+    problems.
+\end{itemize}
+
 \section{Education}
@@
         \item
-          Associate of Arts: Music Studies
-
+          Associate of Arts: Mathematics
         \item
-          Associate of Arts: Mathematics
+          Mathematics and Pre-Engineering Studies:\\
+          Emphasis in Computer Science
       \end{itemize}
@@
           B.S. Applied Mathematics:\\
-          \phantom{B.s. }Emphasis in Computational Science
+          \phantom{B.S. }Emphasis in Computational Science
       \end{itemize}
@@
         \item
-          Senior music and computer science tutor at Mesa college
+          Senior computer science and music tutor at San Diego Mesa college
         \item
-          Covered music theory, ear training, piano, voice, C/C++,
-          Java, C\#, Microsoft VB, Excel and Access
+          Covered C/C++, Java, C\#, Microsoft VB, Excel and Access, music
+          theory, ear training, piano, vocal performance
       \end{itemize}
@@
 
-    \subsection{San Diego City Robotics club (2013--2014)}
+    \subsection{Student Organization Leader}
     \begin{footnotesize}
@@
         \item
-          Served as software team leader
+          Software team leader at San Diego City Robotics club (2013--2014).
+          Participated in
+          \href{http://www.robonation.org/competition/robosub}{RoboSub competition}
         \item
-          Participated in
-          \href{http://www.robonation.org/competition/robosub}{RoboSub
-          competition}, 2014 season
+          Technical advisor at multiple clubs
       \end{itemize}
@@
         \item
-          C/C++, Java, Python, Lua, SQL and \LaTeX
+          C/C++, Java, Python, Lua, SQL and \LaTeX, etc.
       \end{itemize}
@@
         \item
-          Command line, Vim, Git, CMake, Gradle
+          Command line tools like Vim, Git, CMake, Gradle
         \item
-          Major IDEs (Visual Studio, Eclipse, Netbeans, IntelliJ, etc.)
+          Major IDEs like Visual Studio, Eclipse, Netbeans, IntelliJ
       \end{itemize}
@@
 
-\section{Projects}
+\section{Sample work}
 \begin{footnotesize}
@@
     \item
-      \textsc{\href{https://nilsso.github.io}{Website}:}
+      \textsc{\href{https://\username.github.io}{Website}:}\\
       Houses my notes on a wide variety of subjects, including mathematics, music and programming
@@
     \item
-      \textsc{\href{https://github.com/nilsso/ACalculator}{Calcuator project}:}
+      \textsc{\href{https://github.com/\username/ACalculator}{Calcuator project}:}\\
       Final project for Data Structures in C++ class at Mesa
@@
       of responsibility
+
+    \item
+      \textsc{\href{https://github.com/\username/challenge-solutions}{Computational programming challenge solutions}:}\\
+      Efficiently completed dozens of computational programming challenges for websites like
+      \href{https://exercism.io}{exercism.io} and
+      \href{https://projecteuler.net}{Project Euler}.
   \end{itemize}

### 2019-04-24 pages/math/semi-comb/polytope.js
Update

@@ -493,8 +493,8 @@ function initThreeEnvironment() {
     linewidth: 2
   });
 
-  nodeMaterialA = new THREE.MeshBasicMaterial({ color: 0xff0000 });
-  nodeMaterialB = new THREE.MeshBasicMaterial({ color: 0x00ff00 });
+  nodeMaterialA = new THREE.MeshToonMaterial({ color: 0xff0000 });
+  nodeMaterialB = new THREE.MeshToonMaterial({ color: 0x00ff00 });
 
   window.addEventListener('resize', onWindowResize, false);
 }

### 2019-04-24 pages/math/semi-comb/project/paper.tex
Update

\documentclass{amsart}
\usepackage[T1]{fontenc}
\usepackage{mathpazo}
%\usepackage[margin=1in]{geometry}
\usepackage[inline]{enumitem}
%\usepackage{rotating}
%\usepackage{color}
%\usepackage{tabu}
%\usepackage{parskip}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{calc}
\usepackage{xfrac}
\usepackage{mathtools}
\usepackage{cancel}
\usepackage{tikz}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{calc}
%\usepackage{xcolor-solarized}
%\usepackage{minted}
%\usepackage{MnSymbol}
%\usepackage[libertine]{newtxmath}
%\newcommand*\circled[1]{\tikz[baseline= (char.base)]{
    %\node[shape=circle,draw,inner sep=2pt] (char) {#1};}}
%\usepackage{xypic}
%\usepackage[tightpage]{preview} % display
% Math operators
\DeclareMathOperator{\Z}{\mathbb{Z}}
\DeclareMathOperator{\Q}{\mathbb{Q}}
\DeclareMathOperator{\N}{\mathbb{N}}
\DeclareMathOperator{\R}{\mathbb{R}}
\DeclareMathOperator{\C}{\mathbb{C}}
\DeclareMathOperator{\F}{\mathbb{F}}
\DeclareMathOperator{\sge}{\mathsf{e}}
\DeclareMathOperator{\sgm}{\mathsf{m}}
\DeclareMathOperator{\sgG}{\mathsf{G}}
\DeclareMathOperator{\sgg}{\mathsf{g}}
\DeclareMathOperator{\sgF}{\mathsf{F}}
\DeclareMathOperator{\sgt}{\mathsf{t}}
\DeclareMathOperator{\sgL}{\mathsf{L}}
\DeclareMathOperator{\sgZ}{\mathsf{Z}}
\DeclareMathOperator{\sgAp}{Ap}
\DeclareMathOperator{\sgPF}{PF}
\DeclareMathOperator{\sgconv}{conv}
\DeclareMathOperator{\sgsupp}{supp}
\DeclareMathOperator{\calO}{\mathcal{O}}
\DeclareMathOperator{\Grho}{\prescript{}{\rho}G}
% Theorem environments
\theoremstyle{plain}
\newtheorem*{thm}{Theorem}
\newtheorem*{lemma}{Lemma}
\newtheorem*{claim}{Claim}
\newtheorem*{cor}{Corollary}
\newtheorem*{prop}{Proposition}
\newtheorem*{conj}{Conjecture}
\theoremstyle{remark}
\newtheorem*{example}{Example}
\theoremstyle{definition}
\newtheorem*{definition}{Definition}
% Paired math operators
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\DeclarePairedDelimiter{\floor}{\lfloor}{\rfloor}
% Math helper functions
\newcommand{\congr}[2]{{[#1]}_{#2}}
\newcommand{\set}[1]{\{#1\}}
\newcommand{\genset}[1]{{\langle{}#1\rangle{}}}
\newcommand{\abs}[1]{\lvert{}#1\rvert{}}
\newcommand{\norm}[1]{\lVert{}#1\rVert{}}
\newcommand{\bmx}[1]{\begin{bmatrix}#1\end{bmatrix}}
\newcommand{\pmx}[1]{\begin{pmatrix}#1\end{pmatrix}}
  \newcommand{\sbmx}[1]{{\left[\begin{smallmatrix}#1\end{smallmatrix}\right]}}
\newcommand{\smallxymatrix}[2]{\xymatrix@C-=#1cm@R-=#1cm{#2}}
\renewcommand\labelitemi{\small$\bullet$}
\begin{document}
%
%
%
\noindent
\begin{quote}
  (13) \emph{Flow polytopes.}
  A \emph{directed graph} is a collection of dots (called \emph{vertices}) and
  arrow between them (called \emph{edges}). A \emph{flow} on a directed graph is a
  way to label each edge of $G$ by an element of $\Z$ (or $\Z_n$) so that at each
  vertex $v$, the sum of the edges entering $v$ equals the sum of the edges
  leaving $v$ (i.e.\ the in \emph{flow} at each vertex equals the \emph{out
  flow}). The flows on a given directed graph can be counted using a certain
  family of polytopes, whose integer points each coincide with a flow on $G$.
  \\[1em]
  \noindent
  Source:
  \emph{Combinatorial reciprocity theorems} (M. Beck, R. Sanyal), Chapters 1 and 7.
\end{quote}

\hrulefill

% 1.2 Flows on Graphs notes

A graph $G=(V,E)$ is a collection of $V$ a set of vertices and $E$ a set of
edges between these vertices. Now, a graph doesn't have to have any vertices or
any edges (except that if it has edges there must be vertices to which those edges
connect).
Also note that the vertices of a graph can be elements of some arbitrary $\F^n$
space, but for this report we'll only concern ourselves with graphs in $\Z^2$
Euclidean space.
\begin{definition}[Component, connected component]
  A \emph{connected component} (or simply a \emph{component}) of a graph $G$ is
  a subgraph (a subset of the vertices and edges of $G$) in which any two
  vertices are either directed connect via an edge or are connected to
  one-another via a \emph{path} (a series of vertices and edges). A single
  vertex with no connecting edges is in itself a connected component.
\end{definition}
Any graph then is the disjoint union of connected components.
For example figure~\ref{fig:disjoint-union} can be called a single graph that is the disjoint
union of three distinct connected components.
\begin{figure}[h]
  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
    \path
      (.5,.5) node (a) {}
      (0,0) node (b) {} (1,0) node (c) {} (1,1) node (d) {} (0,1) node (e) {}
      (2,1) node (f) {} (2,0) node (g) {} (3,0) node (h) {};
    \draw (a);
    \draw (b) -- (c) -- (d) -- (e) -- (b);
    \draw (f) -- (g) -- (h);
  \end{tikzpicture}
  \caption[Disjoin union]{}
  \label{fig:disjoint-union}
\end{figure}
\begin{lemma}
  A connected component of the graph $G$ is a maximal subgraph of $G$ in which
  any two nodes are connect by a path.
\end{lemma}
\begin{lemma}
  A graph $G$ is \emph{connected} if it has only one connected component.
\end{lemma}
\begin{definition}[Bridge]
  A \emph{bridge} is a single edge which serves as a connection between two connected
  components which if removed would increase the number of connected
  components of the graph by one.
\end{definition}
For example, removing the bridge in figure~\ref{fig:bridge} turns a single
connected component into two triangular connected components:
one single connected graph into a graph with two connected subgraphs.
\begin{figure}[h]
  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
    \path
      (-.5,.5) node (a) {} ($({-(1+sqrt(3))/2},0)$) node (b) {} ($({-(1+sqrt(3))/2},1)$) node (c) {}
      ( .5,.5) node (d) {} ($({ (1+sqrt(3))/2},0)$) node (e) {} ($({ (1+sqrt(3))/2},1)$) node (f) {};
    \draw (a) -- (b) -- (c) -- (a);
    \draw (d) -- (e) -- (f) -- (d);
    \draw[dashed] (a) -- (d);
  \end{tikzpicture}
  \hspace{1cm}
  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
    \path
      (-.5,.5) node (a) {} ($({-(1+sqrt(3))/2},0)$) node (b) {} ($({-(1+sqrt(3))/2},1)$) node (c) {}
      ( .5,.5) node (d) {} ($({ (1+sqrt(3))/2},0)$) node (e) {} ($({ (1+sqrt(3))/2},1)$) node (f) {};
    \draw (a) -- (b) -- (c) -- (a);
    \draw (d) -- (e) -- (f) -- (d);
  \end{tikzpicture}
  \caption[Bridges]{A graph with and without a bridge.}
  \label{fig:bridge}
\end{figure}
So far we've only looked at graph which are \emph{unoriented}.
\begin{definition}[Directed, oriented graph]
  A \emph{directed} or \emph{oriented graph} is a graph is a graph on which we
  define an \emph{orientation} via a subset $\rho$ of the edges $E$ of the
  graph. For each edge $e=v_i v_j\in E$ (connecting the vertices $v_i,v_j\in
  V$) with $i<j$ we direct:
  \[
    v_i\stackrel{e}{\leftarrow}v_j\text{ if }e\in\rho\text{, and }
    v_i\stackrel{e}{\rightarrow}v_j\text{ if }e\notin\rho.
  \]
\end{definition}
This definition may be confusing at first glance because $\rho$
may be missing some of the edges of $E$. What this definition attempts to succinctly
encapsulate is only the edges with their direction pointing from the vertex of higher
index to the vertex of lower index (which does certainly feel backwards),
with all the remaining edges not in $\rho$ directed in the opposite direction,
from lower to higher index.
Figure~\ref{fig:directed-graph} tries to illustrate this encapsulation for a graph
with five vertices and an orientation $\rho=\{14,23,24\}$.
\begin{figure}[h]
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
      \path
        (0,1) node (v_1)[label=left:$v_1$]{}
        (1,1) node (v_2)[label=right:$v_2$]{}
        (1,0) node (v_3)[label=right:$v_3$]{}
        (0,0) node (v_4)[label=left:$v_4$]{};
      \draw (v_4) -- (v_3) -- (v_2) -- (v_1) -- (v_4) -- (v_2);
    \end{tikzpicture}
    \caption{The undirected graph.}
  \end{subfigure}
  %\hspace{1cm}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[
        every node/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \path
        (0,1) node (v_1)[label=left:$v_1$]{}
        (1,1) node (v_2)[label=right:$v_2$]{}
        (1,0) node (v_3)[label=right:$v_3$]{}
        (0,0) node (v_4)[label=left:$v_4$]{};
      \draw[postaction={decorate}] (v_4) -- (v_1);
      \draw[postaction={decorate}] (v_4) -- (v_2);
      \draw[postaction={decorate}] (v_3) -- (v_2);
      \draw (v_3) -- (v_4);
      \draw (v_1) -- (v_2);
    \end{tikzpicture}
    \caption{$\rho$ edges marked.}
  \end{subfigure}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    \begin{tikzpicture}[
        every node/.style={draw,shape=circle,fill=white,inner sep=1},
        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
      ]
      \path
        (0,1) node (v_1)[label=left:$v_1$]{}
        (1,1) node (v_2)[label=right:$v_2$]{}
        (1,0) node (v_3)[label=right:$v_3$]{}
        (0,0) node (v_4)[label=left:$v_4$]{};
      \draw[postaction={decorate}] (v_4) -- (v_1);
      \draw[postaction={decorate}] (v_4) -- (v_2);
      \draw[postaction={decorate}] (v_3) -- (v_2);
      \draw[postaction={decorate}] (v_3) -- (v_4);
      \draw[postaction={decorate}] (v_1) -- (v_2);
    \end{tikzpicture}
    \caption{$E\setminus\rho$ edges marked.}
  \end{subfigure}
  \caption[A directed graph]{A directed graph.}
  \label{fig:directed-graph}
\end{figure}

As an aside, directed graphs are the subject of many algorithms in computer
science, often pertaining to finding optimal ways to traverse the paths of said
graphs. In some models each edge is considered to be of equal ``weight'' as any
other. That is if two edges originating from the same node both point to the
same node, there should be no real preference to traveling down one edge or the
other to get to the destination. On the other hand we might assign a weight to
each edge, presenting a cost-benefit analysis in choosing a path to take (as in
figure~\ref{fig:path-finding} where the edge with weight 5 now becomes most
expensive to traverse versus the one with weight 2).
\begin{figure}[h]
  \begin{tikzpicture}[
    dot/.style={draw,shape=circle,fill=white,inner sep=1},
    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
  ]
    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{} (b);
    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$\phantom 5$} (b);
  \end{tikzpicture}
  \hspace{1cm}
  \begin{tikzpicture}[
    dot/.style={draw,shape=circle,fill=white,inner sep=1},
    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
  ]
    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{$2$} (b);
    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$5$} (b);
  \end{tikzpicture}
  \caption{A directed graph with and without weights.}
  \label{fig:path-finding}
\end{figure}

Intuitively these weights are often simple $\Z$ integers.
But moving on, we now we introduce \emph{flow} values to edges; similar
values to weights, but living not within $\Z$ but instead within an Abelian
group $\Z_n=\sfrac\Z n$. (There may also be optimal path algorithms associated
with flow values, but for this paper our focus is elsewhere.)
\begin{definition}[$\Z_n$-flow]
  A \emph{$\Z_n$-flow} is a map $f:E\to\Z_n$ which to each $e$ edge of $E$
  assigns a flow ${f(e)\in\Z_n}$ such that there is ``conservation of flow'' at
  every $v\in V$ vertex, by which me mean the sum of the flows into a vertex $v$
  is equivalent to the sum of the flows out it:
  \[
    \sum_{\stackrel e \to v}f(e)=\sum_{v\stackrel e \to}f(e).
  \]
\end{definition}
And it's important to note equivalence here since $\sum f(e)\in\Z_n$.
\begin{definition}[$f$ support]
  The \emph{support} of $f$, denoted $\sgsupp(f)$, is the subset of edges $e$
  whose flows are non-zero:
  \[
    \sgsupp(f)=\{e\in E:f(e)\ne 0\}\subseteq E
  \] 
\end{definition}
If $\sgsupp(f)=E$ (all $e$ edges have $f(e)\ne0$), then $f$ is considered
``nowhere-zero''. For the rest of this report we'll be concerned with these
nowhere-zero $\Z_n$-flows, in particular with counting how many of them can be
made for any particular graph and Abelian group.
(So going forward, $G$ will always refer to a graph in $\Z^2$ with $V$ vertices
and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$,
and $\Z_n$ an Abelian group to which $f$ a $\Z_n$-flow maps.)
\begin{definition}
  Define a counting function:
  \[
    \varphi_G(n)=\text{the number of $f$ nowhere-zero $\Z_n$-flows on $G$}
  \] 
\end{definition}
As it happens\ldots
\begin{prop}
  The flow-counting function $\varphi_G(n)$ is independent of the orientation
  $\rho$ of $G$.
\end{prop}
(Todo:? Describe the proof of this proposition.)
\begin{lemma}
  $G$ will not have any nowhere-zero flow if $G$ has a \emph{bridge}---an edge
  whose removal increases the number of connected components of $G$.
\end{lemma}

% 7.6 Graph Flows and Totally Cyclic Orientations notes

%
%
%
\end{document}

### 2019-04-24 pages/math/semi-comb/project/paper.tex
Update

@@
 %
+
 \noindent
@@
 
-A graph $G=(V,E)$ is a collection of $V$ a set of vertices and $E$ a set of
-edges between these vertices. Now, a graph doesn't have to have any vertices or
-any edges (except that if it has edges there must be vertices to which those edges
-connect).
-Also note that the vertices of a graph can be elements of some arbitrary $\F^n$
-space, but for this report we'll only concern ourselves with graphs in $\Z^2$
-Euclidean space.
+A graph $G=(V,E)$ is a collection of $V$, a set of vertices, and $E$, a set of
+edges between the vertices. Now, a graph doesn't have to have any vertices, nor
+does it have to to have any edges (except that if it has edges there must be
+vertices to which those edges connect).
+Also note that the vertices of a graph can be elements of some arbitrary
+d-dimensional space, but for this report we'll only concern ourselves with
+graphs in some two-dimensional space.
 \begin{definition}[Component, connected component]
@@
   a subgraph (a subset of the vertices and edges of $G$) in which any two
-  vertices are either directed connect via an edge or are connected to
+  vertices are either directly connected via an edge or are connected to
   one-another via a \emph{path} (a series of vertices and edges). A single
@@
 \begin{figure}[h]
-  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
+  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=black,inner sep=1}]
     \path
@@
   A \emph{bridge} is a single edge which serves as a connection between two connected
-  components which if removed would increase the number of connected
+  components which, if removed, would increase the number of connected
   components of the graph by one.
@@
   \hspace{1cm}
-  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
+  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=black,inner sep=1}]
     \path
@@
 \end{figure}
-So far we've only looked at graph which are \emph{unoriented}.
+So far we've only looked at \emph{unoriented} graphs, but
+now we introduce directions within graphs.
 \begin{definition}[Directed, oriented graph]
-  A \emph{directed} or \emph{oriented graph} is a graph is a graph on which we
+  A \emph{directed} or \emph{oriented graph} is a graph on which we
   define an \emph{orientation} via a subset $\rho$ of the edges $E$ of the
@@
     \centering
-    \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
+    \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=black,inner sep=1}]
       \path
@@
     \begin{tikzpicture}[
-        every node/.style={draw,shape=circle,fill=white,inner sep=1},
+        every node/.style={draw,shape=circle,fill=black,inner sep=1},
         decoration={markings,mark=at position 0.5 with {\arrow{>}}}
@@
   \begin{tikzpicture}[
-    dot/.style={draw,shape=circle,fill=white,inner sep=1},
+    dot/.style={draw,shape=circle,fill=black,inner sep=1},
     decoration={markings,mark=at position 0.5 with {\arrow{>}}}
@@
 
+\begin{figure}[h]
+  \begin{subfigure}[t]{.3\textwidth}
+    \begin{tikzpicture}[
+        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
+        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
+        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
+      ]
+      \draw (0,0) node[gdot](a){} -- (1,0) node[gdot](b){};
+      \node[ddot](c) at (.5,-.5) {};
+      \draw (c) to [out=180,in=90,looseness=60] (c);
+    \end{tikzpicture}
+    \caption{Simplest graph with a bridge.}
+  \end{subfigure}
+  \begin{subfigure}[t]{.3\textwidth}
+    \begin{tikzpicture}[
+        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
+        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
+        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
+      ]
+      \draw (0,0) node[gdot]{} -- (1,0) node[gdot]{} -- ($(1/2,{sqrt(3)/2})$) node [gdot]{} -- cycle;
+      \node[ddot] (a) at ($(1/2,{-sqrt(2)/3})$) {};
+      \node[ddot] (b) at ($(1/2,{sqrt(3)/6})$) {};
+      \draw (a) -- (b);
+      \draw (a) to [out=180,in=135,looseness=4] (b);
+      \draw (a) to [out=0,in=45,looseness=4] (b);
+    \end{tikzpicture}
+    \caption{A complete graph.}
+  \end{subfigure}
+  \begin{subfigure}[t]{.3\textwidth}
+    \begin{tikzpicture}[
+      gdot/.style={draw,shape=circle,fill=black,inner sep=1},
+      ddot/.style={draw,shape=circle,fill=white,inner sep=1},
+      decoration={markings,mark=at position 0.5 with {\arrow{>}}}
+    ]
+      \draw (0,0) node[gdot]{} -- (0,1) node[gdot]{};
+      \draw (0,0) node[gdot]{} -- ($({sqrt(3)/2},1/2)$) node[gdot]{} -- (0,1) node[gdot]{} -- ($({-sqrt(3)/2},1/2)$) node[gdot]{} -- cycle;
+      \node[ddot] (a) at (0,-1/2){};
+      \node[ddot] (b) at ($({-sqrt(3)/6},1/2)$){};
+      \node[ddot] (c) at ($({ sqrt(3)/6},1/2)$){};
+      \draw (a) to [out=135,in=240] (b);
+      \draw (a) to [out=180,in=120,looseness=4] (b);
+      \draw (a) to [out=45,in=300] (c);
+      \draw (a) to [out=0,in=60,looseness=4] (c);
+      \draw (b) -- (c);
+    \end{tikzpicture}
+    \caption{Graph with two connected components.}
+  \end{subfigure}
+  \caption{Various graphs and their duals.}
+  \label{fig:graphs-and-duals}
+\end{figure}
+
 % 7.6 Graph Flows and Totally Cyclic Orientations notes

### 2019-04-24 pages/math/semi-comb/project/paper.tex
Update

@@
 \renewcommand\labelitemi{\small$\bullet$}
+%
+\tikzstyle{gdot}=[draw,shape=circle,fill=black,inner sep=1]
+\tikzstyle{ddot}=[draw,shape=circle,fill=white,inner sep=1]
 \begin{document}
@@
 A graph $G=(V,E)$ is a collection of $V$, a set of vertices, and $E$, a set of
-edges between the vertices. Now, a graph doesn't have to have any vertices, nor
+edges between the vertices.
+Now, a graph doesn't have to have any vertices, nor
 does it have to to have any edges (except that if it has edges there must be
 vertices to which those edges connect).
-Also note that the vertices of a graph can be elements of some arbitrary
+Also note that the nodes of a graph can be elements of some arbitrary
 d-dimensional space, but for this report we'll only concern ourselves with
 graphs in some two-dimensional space.
+(Note that the word ``node'' is analogous to ``vertex'' and that this paper
+will do plenty of haphazard switching between the two of them.)
 \begin{definition}[Component, connected component]
@@
 connected component into two triangular connected components:
-one single connected graph into a graph with two connected subgraphs.
+one complete graph into a graph with two complete subgraphs.
 \begin{figure}[h]
@@
 (So going forward, $G$ will always refer to a graph in $\Z^2$ with $V$ vertices
-and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$,
+and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$
 and $\Z_n$ an Abelian group to which $f$ a $\Z_n$-flow maps.)
@@
 (Todo:? Describe the proof of this proposition.)
-\begin{lemma}
+\begin{prop}
   $G$ will not have any nowhere-zero flow if $G$ has a \emph{bridge}---an edge
   whose removal increases the number of connected components of $G$.
-\end{lemma}
+\end{prop}
 
+Now we introduce the concept of the \emph{dual graph} of a graph. Consider a
+graph $G$ as subdividing the plane into discrete regions; if two points lie
+within a region then they can be connected without intersecting an edge of $G$.
+Regions which are neighbors have an edge of $G$ which separate them
+(their topological closures sharing a proper 1-dimensional part of their
+boundaries).
+\begin{definition}[Dual graph]
+  The \emph{dual graph} of a graph $G$ is the graph $G^*=(V^*,E^*)$ with
+  vertices corresponding to the regions of $G$.
+  Two $V^*$ vertices are connected via edge $e^*\in E^*$ if an original edge $e$
+  of $G$ is properly contained within the boundaries of their corresponding
+  regions.
+\end{definition}
+Figure~\ref{fig:dual-incomplete} shows a graph with four vertices (solid)
+along with the vertices (hollow) of its dual to demonstrate the regions which
+$G$ subdivides the plane into.
+(However the edges are omitted.
+See figure~\ref{fig:graphs-and-duals} for complete illustrations of graphs and
+their duals.)
+\begin{figure}[h]
+    \begin{tikzpicture}
+      \path
+        (0,0) node (a)[gdot]{}
+        (1,0) node (b)[gdot]{}
+        (1,1) node (c)[gdot]{}
+        (0,1) node (d)[gdot]{};
+      \draw (a) -- (b) -- (c) -- (d) -- (a);
+      \path (.5,.5) node[ddot]{} (1.5,.5) node[ddot]{};
+  \end{tikzpicture}
+  \caption{A graph and its (incompletely portrayed) dual graph.}
+  \label{fig:dual-incomplete}
+\end{figure}
+
+Another way to think of the $e^*$ edges is that there is one for every edge $e$
+that bounds two regions of $G$ (connecting the $G^*$ vertices corresponding to
+the two regions), and that $e^*$ crosses-over its corresponding $e$ edge.
+Figure~\ref{fig:graphs-and-duals} illustrates some examples of graphs
+(with solid dot vertices) and their duals (with hollow dot vertices).
 \begin{figure}[h]
@@
 
+What naturally follows is that if $G$ is a directed graph, we should want
+$G^*$ to also be some sort of directed graph.
+So, given an orientation of $G$, an orientation on $G^*$ can be induced by
+``rotating'' the direction of the edge clockwise. That is, the dual edge $e^*$
+will ``point'' east assuming that the primal edge $e$ points north:
+\begin{figure}[h]
+  \begin{tikzpicture}
+    \draw[->,thick] (.25,0) .. controls (.25,.5) and (.75,.5) .. (.75,1);
+    \draw[->] (0,.5) -- (1,.5);
+  \end{tikzpicture}
+  \hspace{1cm}
+  \begin{tikzpicture}
+    \draw[<-,thick] (.25,0) .. controls (.25,.5) and (.75,.5) .. (.75,1);
+    \draw[<-] (0,.5) -- (1,.5);
+  \end{tikzpicture}
+\end{figure}
+
 % 7.6 Graph Flows and Totally Cyclic Orientations notes

### 2019-05-05 pages/math/semi-comb/project/paper.tex
Update

--- 2019-04-24 pages/math/semi-comb/project/paper.tex
@@
 \usepackage[T1]{fontenc}
-\usepackage{mathpazo}
+%\usepackage{mathpazo}
 %\usepackage[margin=1in]{geometry}
@@
 \usepackage{cancel}
+\usepackage{framed}
+\usepackage{nth}
 \usepackage{tikz}
-\usetikzlibrary{decorations.markings}
-\usetikzlibrary{calc}
+\usetikzlibrary{calc,decorations.markings}
 %\usepackage{xcolor-solarized}
@@
 \DeclareMathOperator{\sgsupp}{supp}
+\DeclareMathOperator{\calC}{\mathcal{C}}
+\DeclareMathOperator{\calF}{\mathcal{F}}
 \DeclareMathOperator{\calO}{\mathcal{O}}
@@
 \theoremstyle{plain}
-\newtheorem*{thm}{Theorem}
-\newtheorem*{lemma}{Lemma}
+\newtheorem{thm}{Theorem}
+\newtheorem*{thm*}{Theorem}
+\newtheorem{lemma}{Lemma}
+\newtheorem*{lemma*}{Lemma}
 \newtheorem*{claim}{Claim}
@@
 \theoremstyle{remark}
-\newtheorem*{example}{Example}
+\newtheorem*{example*}{Example}
 \theoremstyle{definition}
-\newtheorem*{definition}{Definition}
+\newtheorem*{definition*}{Definition}
+% Special theorem displays
+\newenvironment{example}%
+	{\begin{leftbar}\begin{example*}
+}{%
+	\end{example*}\end{leftbar}
+}
+\newenvironment{definition}%
+	{\begin{leftbar}\begin{definition*}
+}{%
+	\end{definition*}\end{leftbar}
+}
 % Paired math operators
@@
   \newcommand{\sbmx}[1]{{\left[\begin{smallmatrix}#1\end{smallmatrix}\right]}}
-\newcommand{\smallxymatrix}[2]{\xymatrix@C-=#1cm@R-=#1cm{#2}}
+\newcommand{\smallxymatrix}[2]{\xymatrix@C-=#1in@R-=#1in{#2}}
 \renewcommand\labelitemi{\small$\bullet$}
+%
+%\makeatletter
+\tikzset{%
+  gdot/.style={draw,shape=circle,fill=black,inner sep=1},
+  ddot/.style={draw,shape=circle,fill=white,inner sep=1},
+  dedge/.style={draw=black!40},
+  midarrow/.style={postaction={decorate},decoration={markings,mark=at position 0.5 with {\arrow{>}}}}
+}
+%\makeatother
 \begin{document}
@@
 %
+
+\section*{Prompt:}
+
 \noindent
@@
 
-% 1.2 Flows on Graphs notes
+Graphs are a major area of concern in mathematics, having an entire field to
+study dedicated to them. Many different families of graphs exist, but for this
+paper we'll concern ourselves with directed graphs and $\Z_n$-flows on these
+graphs, all concepts which the first section introduces. The second section
+is dedicated to a reciprocity expression for counting the number of possible
+flows on directed graphs, and to developing some insight into it and its proof.
 
-A graph $G=(V,E)$ is a collection of $V$ a set of vertices and $E$ a set of
-edges between these vertices. Now, a graph doesn't have to have any vertices or
-any edges (except that if it has edges there must be vertices to which those edges
-connect).
-Also note that the vertices of a graph can be elements of some arbitrary $\F^n$
-space, but for this report we'll only concern ourselves with graphs in $\Z^2$
-Euclidean space.
+% ------------------------------------------------------------------------------
+% 1.2
+% ------------------------------------------------------------------------------
+
+\section{Introduction to graphs and flows}
+
+\subsection{Graphs}
+
+A graph $G=(V,E)$ is a collection of $V$, a set of vertices, and $E$, a set of
+edges between the vertices.
+Now, a graph doesn't have to have any vertices, nor
+does it have to to have any edges (except that if it has edges there must be
+vertices to which those edges connect).
+Also note that the nodes of a graph can be elements of some arbitrary
+d-dimensional space, but for this report we'll only concern ourselves with
+graphs in some two-dimensional space.
+(Note that the word ``node'' is analogous to ``vertex'' and that this paper
+will do plenty of haphazard switching between the two of them.)
 \begin{definition}[Component, connected component]
@@
 Any graph then is the disjoint union of connected components.
-For example figure~\ref{fig:disjoint-union} can be called a single graph that is the disjoint
+For example Figure~\ref{fig:disjoint-union} can be called a single graph that is the disjoint
 union of three distinct connected components.
-\begin{figure}[h]
-  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
+\begin{figure}[ht]
+  \begin{tikzpicture}[every node/.style=gdot]
     \path
@@
 \end{figure}
-\begin{lemma}
+\begin{lemma*}
   A connected component of the graph $G$ is a maximal subgraph of $G$ in which
   any two nodes are connect by a path.
-\end{lemma}
-\begin{lemma}
+\end{lemma*}
+\begin{lemma*}
   A graph $G$ is \emph{connected} if it has only one connected component.
-\end{lemma}
+\end{lemma*}
 \begin{definition}[Bridge]
   A \emph{bridge} is a single edge which serves as a connection between two connected
-  components which if removed would increase the number of connected
+  components which, if removed, would increase the number of connected
   components of the graph by one.
 \end{definition}
-For example, removing the bridge in figure~\ref{fig:bridge} turns a single
+For example, removing the bridge in Figure~\ref{fig:bridge} turns a single
 connected component into two triangular connected components:
-one single connected graph into a graph with two connected subgraphs.
-\begin{figure}[h]
-  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
+one complete graph into a graph with two complete subgraphs.
+\begin{figure}[ht]
+  \begin{tikzpicture}[every node/.style=gdot]
     \path
@@
   \end{tikzpicture}
-  \hspace{1cm}
-  \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
+  \hspace{1in}
+  \begin{tikzpicture}[every node/.style=gdot]
     \path
@@
 \end{figure}
-So far we've only looked at graph which are \emph{unoriented}.
+
+\subsection{Directed graphs}
+
+So far we've only looked at \emph{unoriented} graphs, but
+now we introduce a notion of direction, or orientation, to graphs.
 \begin{definition}[Directed, oriented graph]
-  A \emph{directed} or \emph{oriented graph} is a graph is a graph on which we
+  A \emph{directed} or \emph{oriented graph} is a graph on which we
   define an \emph{orientation} via a subset $\rho$ of the edges $E$ of the
@@
 with five vertices and an orientation $\rho=\{14,23,24\}$.
-\begin{figure}[h]
+\begin{figure}[ht]
   \begin{subfigure}[t]{0.3\textwidth}
     \centering
-    \begin{tikzpicture}[every node/.style={draw,shape=circle,fill=white,inner sep=1}]
+    \begin{tikzpicture}[every node/.style=gdot]
       \path
@@
   \end{subfigure}
-  %\hspace{1cm}
+  %\hspace{1in}
   \begin{subfigure}[t]{0.3\textwidth}
     \centering
-    \begin{tikzpicture}[
-        every node/.style={draw,shape=circle,fill=white,inner sep=1},
-        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
-      ]
+    \begin{tikzpicture}[every node/.style=gdot]
       \path
@@
         (0,0) node (v_4)[label=left:$v_4$]{};
-      \draw[postaction={decorate}] (v_4) -- (v_1);
-      \draw[postaction={decorate}] (v_4) -- (v_2);
-      \draw[postaction={decorate}] (v_3) -- (v_2);
+      \draw[midarrow] (v_4) -- (v_1);
+      \draw[midarrow] (v_4) -- (v_2);
+      \draw[midarrow] (v_3) -- (v_2);
       \draw (v_3) -- (v_4);
@@
     \centering
-    \begin{tikzpicture}[
-        every node/.style={draw,shape=circle,fill=white,inner sep=1},
-        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
-      ]
+    \begin{tikzpicture}[every node/.style={gdot}]
       \path
@@
         (0,0) node (v_4)[label=left:$v_4$]{};
-      \draw[postaction={decorate}] (v_4) -- (v_1);
-      \draw[postaction={decorate}] (v_4) -- (v_2);
-      \draw[postaction={decorate}] (v_3) -- (v_2);
-      \draw[postaction={decorate}] (v_3) -- (v_4);
-      \draw[postaction={decorate}] (v_1) -- (v_2);
+      \draw[midarrow] (v_4) -- (v_1);
+      \draw[midarrow] (v_4) -- (v_2);
+      \draw[midarrow] (v_3) -- (v_2);
+      \draw[midarrow] (v_3) -- (v_4);
+      \draw[midarrow] (v_1) -- (v_2);
     \end{tikzpicture}
@@
 each edge, presenting a cost-benefit analysis in choosing a path to take (as in
-figure~\ref{fig:path-finding} where the edge with weight 5 now becomes most
+Figure~\ref{fig:path-finding} where the edge with weight 5 now becomes most
 expensive to traverse versus the one with weight 2).
-\begin{figure}[h]
-  \begin{tikzpicture}[
-    dot/.style={draw,shape=circle,fill=white,inner sep=1},
-    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
-  ]
-    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
-    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{} (b);
-    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$\phantom 5$} (b);
+\begin{figure}[ht]
+  \begin{tikzpicture}
+    \path (0,0) node[gdot] (a){} (2,0) node[gdot] (b){};
+    \draw[midarrow] (a) to [out=45, in=135] node[above]{} (b);
+    \draw[midarrow] (a) to [out=315,in=225] node[below]{$\phantom 5$} (b);
   \end{tikzpicture}
-  \hspace{1cm}
-  \begin{tikzpicture}[
-    dot/.style={draw,shape=circle,fill=white,inner sep=1},
-    decoration={markings,mark=at position 0.5 with {\arrow{>}}}
-  ]
-    \path (0,0) node[dot] (a){} (2,0) node[dot] (b){};
-    \draw[postaction=decorate] (a) to [out=45, in=135] node[above]{$2$} (b);
-    \draw[postaction=decorate] (a) to [out=315,in=225] node[below]{$5$} (b);
+  \hspace{1in}
+  \begin{tikzpicture}
+    \path (0,0) node[gdot] (a){} (2,0) node[gdot] (b){};
+    \draw[midarrow] (a) to [out=45, in=135] node[above]{$2$} (b);
+    \draw[midarrow] (a) to [out=315,in=225] node[below]{$5$} (b);
   \end{tikzpicture}
@@
 \end{figure}
+Intuitively these weights are often simple $\Z$ integers.
 
-Intuitively these weights are often simple $\Z$ integers.
-But moving on, we now we introduce \emph{flow} values to edges; similar
+\subsection{Flows}
+
+Moving on we introduce \emph{flow} values to edges; similar
 values to weights, but living not within $\Z$ but instead within an Abelian
-group $\Z_n=\sfrac\Z n$. (There may also be optimal path algorithms associated
-with flow values, but for this paper our focus is elsewhere.)
+group $\Z_n=\sfrac\Z n$.
+%(There may also be optimal path algorithms associated
+%with flow values, similar to weights on directed edges, but for this paper our
+%focus is elsewhere.)
 \begin{definition}[$\Z_n$-flow]
@@
 \end{definition}
-And it's important to note equivalence here since $\sum f(e)\in\Z_n$.
+(And it's important to note equivalence here since $\sum f(e)\in\Z_n$.)
+These functions and more specifically counting them will be the ultimate
+purpose of this paper.
 \begin{definition}[$f$ support]
@@
 made for any particular graph and Abelian group.
-(So going forward, $G$ will always refer to a graph in $\Z^2$ with $V$ vertices
-and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$,
-and $\Z_n$ an Abelian group to which $f$ a $\Z_n$-flow maps.)
+%
+Figure~\ref{fig:graph-flows} illustrates two different but satisfactory
+$\Z_5$-flows on a graph. Without the context of the Abelian group $Z_5$
+these flows wouldn't seem to work, but, since $3+2\equiv 0\bmod 5$,
+the top and bottom left vertices both have conservation of flow
+equal to zero.
+\begin{figure}[ht]
+  \begin{tikzpicture}
+    \path
+      (0,1) node (a)[gdot]{}
+      ($({cos(  -pi/6 r)},{sin(  -pi/6 r)})$) node (b)[gdot]{}
+      ($({cos(-5*pi/6 r)},{sin(-5*pi/6 r)})$) node (c)[gdot]{};
+    \draw[midarrow] (a) -- node[right]{0} (b);
+    \draw[midarrow] (a) -- node[left]{0} (c);
+    \draw[midarrow] (b) -- node[below]{0} (c);
+  \end{tikzpicture}
+  \hspace{1in}
+  \begin{tikzpicture}
+    \path
+      (0,1) node (a)[gdot]{}
+      ($({cos(  -pi/6 r)},{sin(  -pi/6 r)})$) node (b)[gdot]{}
+      ($({cos(-5*pi/6 r)},{sin(-5*pi/6 r)})$) node (c)[gdot]{};
+    \draw[midarrow] (a) -- node[right]{2} (b);
+    \draw[midarrow] (a) -- node[left]{3} (c);
+    \draw[midarrow] (b) -- node[below]{2} (c);
+  \end{tikzpicture}
+  \caption{An everywhere-zero $\Z_5$-flow and a nowhere-zero $\Z_5$-flow.}
+  \label{fig:graph-flows}
+\end{figure}
+
+Going forward, $G$ will always refer to a 2-dimensional graph with $V$ vertices
+and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$
+and $\Z_n$ to an Abelian group to which $f$ a $\Z_n$-flow maps.
 \begin{definition}
@@
 \end{prop}
-(Todo:? Describe the proof of this proposition.)
-\begin{lemma}
+(The proof of this is a ``left to the reader'' exercise in the original paper.)
+\begin{prop}
   $G$ will not have any nowhere-zero flow if $G$ has a \emph{bridge}---an edge
   whose removal increases the number of connected components of $G$.
-\end{lemma}
+\end{prop}
 
-% 7.6 Graph Flows and Totally Cyclic Orientations notes
+\subsection{Dual graphs}
+
+Consider a graph $G$ as subdividing the plane into connected regions. If two
+points lie within a region then they can be connected without intersecting an
+edge of $G$. Regions which are neighbors have an edge of $G$ which separate them
+(their topological closures sharing a proper 1-dimensional part of their
+boundaries).
+\begin{definition}[Dual graph]
+  The \emph{dual graph} of a graph $G=(V,E)$ is the graph $G^*=(V^*,E^*)$ with
+  vertices corresponding to the regions of $G$.
+  %
+  Two vertices $u^*,v^*\in V^*$
+  which correspond to two regions $R_{u^*}$ and $R_{v^*}$ of $G$ are connected via edge $e^*\in
+  E^*$ if an original edge $e\in E$ is properly contained within the boundaries
+  of $R_{u^*}$ and $R_{v^*}$.
+\end{definition}
+%Figure~\ref{fig:dual-incomplete} shows a graph with four vertices (solid)
+%along with the vertices (hollow) of its dual to demonstrate the regions which
+%$G$ subdivides the plane into.
+%(However the edges are omitted.
+%See Figure~\ref{fig:graphs-and-duals} for complete illustrations of graphs and
+%their duals.)
+%\begin{figure}[ht]
+    %\begin{tikzpicture}
+      %\path
+        %(0,0) node (a)[gdot]{}
+        %(1,0) node (b)[gdot]{}
+        %(1,1) node (c)[gdot]{}
+        %(0,1) node (d)[gdot]{};
+      %\draw (a) -- (b) -- (c) -- (d) -- (a);
+      %\path (.5,.5) node[ddot]{} (1.5,.5) node[ddot]{};
+  %\end{tikzpicture}
+  %\caption{A graph and its (incompletely portrayed) dual graph.}
+  %\label{fig:dual-incomplete}
+%\end{figure}
+In other words there is one $e^*$ for
+every edge $e$ that lies between two regions of $G$; it connects the $G^*$
+vertices corresponding to the two regions; and it crosses over its
+corresponding $e$ edge ($e$ and $e^*$ intersect).
+%
+But as a single illustration says a thousand words,
+Figure~\ref{fig:graphs-and-duals} illustrates a few examples of graphs
+(solid dot vertices) and their duals (hollow dot vertices).
+\begin{figure}[ht]
+  \begin{subfigure}[t]{.3\textwidth}
+    \begin{tikzpicture}[
+        gdot/.style={draw,shape=circle,fill=black,inner sep=1},
+        ddot/.style={draw,shape=circle,fill=white,inner sep=1},
+        decoration={markings,mark=at position 0.5 with {\arrow{>}}}
+      ]
+      \begin{scope}
+        %\clip (-2,-1) rectangle (2,2);
+        \draw (0,0) node[gdot](a){} -- (1,0) node[gdot](b){};
+        \node[ddot](c) at (.5,-.5) {};
+        \draw[dedge] (c) to [out=180,in=90,looseness=60] (c);
+      \end{scope}
+    \end{tikzpicture}
+    \caption{Simplest graph with a bridge.}
+  \end{subfigure}
+  %\begin{subfigure}[t]{.3\textwidth}
+    %\begin{tikzpicture}[
+        %gdot/.style={draw,shape=circle,fill=black,inner sep=1},
+        %ddot/.style={draw,shape=circle,fill=white,inner sep=1},
+        %decoration={markings,mark=at position 0.5 with {\arrow{>}}}
+      %]
+      %\begin{scope}
+        %%\clip (-2,-1) rectangle (2,2);
+        %\draw (0,0) node[gdot]{} -- (1,0) node[gdot]{} -- ($(1/2,{sqrt(3)/2})$) node [gdot]{} -- cycle;
+        %\node[ddot] (a) at ($(1/2,{-sqrt(2)/3})$) {};
+        %\node[ddot] (b) at ($(1/2,{sqrt(3)/6})$) {};
+        %\draw[dedge] (a) -- (b);
+        %\draw[dedge] (a) to [out=180,in=135,looseness=4] (b);
+        %\draw[dedge] (a) to [out=0,in=45,looseness=4] (b);
+      %\end{scope}
+    %\end{tikzpicture}
+    %\caption{A complete graph.}
+  %\end{subfigure}
+  %\begin{subfigure}[t]{.3\textwidth}
+    %\begin{tikzpicture}[
+      %gdot/.style={draw,shape=circle,fill=black,inner sep=1},
+      %ddot/.style={draw,shape=circle,fill=white,inner sep=1},
+      %decoration={markings,mark=at position 0.5 with {\arrow{>}}}
+    %]
+    %\begin{scope}
+      %%\clip (-2,-1) rectangle (2,2);
+      %\draw (0,0) node[gdot]{} -- (0,1) node[gdot]{};
+      %\draw (0,0) node[gdot]{} -- ($({sqrt(3)/2},1/2)$) node[gdot]{} -- (0,1) node[gdot]{} -- ($({-sqrt(3)/2},1/2)$) node[gdot]{} -- cycle;
+      %\node[ddot] (a) at (0,-1/2){};
+      %\node[ddot] (b) at ($({-sqrt(3)/6},1/2)$){};
+      %\node[ddot] (c) at ($({ sqrt(3)/6},1/2)$){};
+      %\draw[dedge] (a) to [out=120,in=240] (b);
+      %\draw[dedge] (a) to [out=180,in=120,looseness=4] (b);
+      %\draw[dedge] (a) to [out=60,in=300] (c);
+      %\draw[dedge] (a) to [out=0,in=60,looseness=4] (c);
+      %\draw[dedge] (b) -- (c);
+    %\end{scope}
+    %\end{tikzpicture}
+    %\caption{Graph with two connected components.}
+  %\end{subfigure}
+  \caption{Various graphs and their duals.}
+  \label{fig:graphs-and-duals}
+\end{figure}
+
+What naturally follows is that if $G$ is a directed graph, we should want
+$G^*$ to also be some sort of directed graph.
+So, given an orientation of $G$, an orientation on $G^*$ can be induced by
+``rotating'' the direction of the edge clockwise. That is, the dual edge $e^*$
+will ``point'' east assuming that the primal edge $e$ points north.
+%\begin{figure}[ht]
+  %\begin{tikzpicture}
+    %\draw[->,thick] (.25,0) .. controls (.25,.5) and (.75,.5) .. (.75,1);
+    %\draw[->,dedge] (0,.5) -- (1,.5);
+  %\end{tikzpicture}
+	%\hspace{1in}
+  %\begin{tikzpicture}
+    %\draw[<-,thick] (.25,0) .. controls (.25,.5) and (.75,.5) .. (.75,1);
+    %\draw[<-,dedge] (0,.5) -- (1,.5);
+  %\end{tikzpicture}
+%\end{figure}
+
+% ------------------------------------------------------------------------------
+% 7.6
+% ------------------------------------------------------------------------------
+\pagebreak
+\section{Reciprocity in counting graph flows}
+
+Ultimately the purpose of this report is in providing some intuition into the
+following theorem and its proof:
+\begin{thm}\label{thm:1.2.5}
+  Let $G$ be a bridgeless graph. For every positive integer $n$, the
+  reciprocity statement:
+  \[
+    {(-1)}^{\xi(G)}\varphi_G(-n)
+  \]
+  counts the number of pairs $(f,p)$,
+  where $f$ is a $\Z_n$-flow and $\rho$ is a totally-cyclic reorientation of
+  $G/\sgsupp(f)$. In particular, when $n=-1$, the statement equals the
+  number of totally-cyclic orientations of $G$.
+\end{thm}
+
+Going forward we'll attempt to build some insight into theorem~\ref{thm:1.2.5}
+and its proof, and into the propositions upon which the proof relies.
+
+\subsection{Flows and flow spaces}
+
+As a matter of notation, for a vertex $v$, $uv$ is a directed edge pointing
+either from a vertex $u$ towards $v$, or from $v$ to $u$. Now to slightly mangle
+a previous definition, we now define flows, as opposed to $Z_n$-flows:
+\begin{definition}[Flow]
+  For $G=(V,E)$ a graph and $\Z_n$ an Abelian group, we define a
+  \emph{nowhere-zero flow}, $f:E\to\Z$, to be a map such that $0<f(e)<n$ for all
+  $e\in E$, and which for all $v\in V$ with an integer $b_v$ (corresponding to
+  $v$) satisfies the equation:
+  \[
+    \sum_{u\to v}f(uv)-\sum_{v\to u}f(uv)=nb_v.
+  \] 
+\end{definition}
+This should appear very similar to the conservation equation in the
+definition of $\Z_n$-flow functions,
+but the distinction is that $\Z_n$-flows map to $\Z_n$ and flows map to $\Z$.
+Nevertheless, since the difference of the sums in the equation of the definition
+above is equal to a multiple of $n$, the sums are indeed congruent modulo $n$,
+similar to the conservation in the definition of $\Z_n$-flows.
+(I'll present the justification for this distinction between $\Z_n$-flows and
+flows soon.)
+
+Next we introduce a specific space of these function
+(as well as further mangle the definition of the $f$ flow ``functions''!):
+\begin{definition}
+  For $\vec b\in\Z^V$ a vector, we define $\calF_G(\vec b)\subseteq\R^E$ to be
+  the affine subspace of all $f\in\R^E$ satisfying the equation of the previous
+  definition but specifically for $n=1$.
+\end{definition}
+What I meant by further mangle is that now we don't consider $f$ only as
+a function, but now also as a coordinate in $\R^E$ space.
+What is $\R^E$ space you ask?
+It is ${\lvert E\rvert}$-dimensional, but we don't call it $\Z^{\lvert E\rvert}$
+space because: each component of a coordinate is indexed by the edges themselves
+as opposed to a more familiar scheme such as $x_1,x_2,x_3,\ldots$.
+
+I certainly had a hard time processing this dual representation, so I'll
+attempt to give a brief example to explain this relationship from function to
+coordinate:
+\begin{example}
+  Fix $G$ a directed graph with four edges, $E=\{e_a,e_b,e_c,e_d\}$,
+  and $f\in\Z^E$ a nowhere-zero flow on $G$ for some Abelian group $\Z_n$.
+  Suppose $f$, being a coordinate in $\Z^E$ space,
+  is the coordinate $(4,2,7,5)$ which maps the edges of the graph in the order
+  as they appear above.
+  Here then is a sort of condensing of $f$'s various representation:
+  \[
+    f=(4,2,7,5)\in\Z^4,~f(e)\in\{4,2,7,5\}
+  \]
+	And then the action of mapping:
+  \[
+    f(e_a)=4,~f(e_b)=2,~f(e_c)=7,~f(e_d)=5
+  \]
+\end{example}
+But what prompts/justifies this mangling of definitions?
+Well, what is ultimately being sought after is a way to relate $\Z_n$-flow
+functions to lattice points in/on some polytope, and vice versa:
+%
+flows $f$ which are points in $n{(0,1)}^E\cap \Z^E$.
+(Note that $n{(0,1)}^E$ is the n'th dilation of all real-valued points contained
+within the ${\lvert E\rvert}$-dimensional open unit cube---no points on the
+boundaries. Then the intersection with $\Z^E$ yields only those points that are
+lattice/integer point.)
+
+\begin{definition}[Flow space]
+  $\calF_G(\vec 0)$ is the \emph{flow space} of $G$ such that each $f$
+  satisfies the conservation equation:
+  \[
+    \sum_{u\to v}f(uv)=\sum_{v\to u}f(uv).
+  \] 
+\end{definition}
+This should now look very familiar to $Z_n$-flows, which from the get-go were
+defined with conservation of flow.
+
+(And eventually I get to actually talking about theorem~\ref{thm:1.2.5}!)
 

### 2019-05-17 pages/math/semi-comb/project/paper.tex
Lazy update

@@
 \DeclareMathOperator{\F}{\mathbb{F}}
-\DeclareMathOperator{\sge}{\mathsf{e}}
-\DeclareMathOperator{\sgm}{\mathsf{m}}
-\DeclareMathOperator{\sgG}{\mathsf{G}}
-\DeclareMathOperator{\sgg}{\mathsf{g}}
-\DeclareMathOperator{\sgF}{\mathsf{F}}
-\DeclareMathOperator{\sgt}{\mathsf{t}}
-\DeclareMathOperator{\sgL}{\mathsf{L}}
-\DeclareMathOperator{\sgZ}{\mathsf{Z}}
+\DeclareMathOperator{\sfe}{\mathsf{e}}
+\DeclareMathOperator{\sfg}{\mathsf{g}}
+\DeclareMathOperator{\sfm}{\mathsf{m}}
+\DeclareMathOperator{\sft}{\mathsf{t}}
+\DeclareMathOperator{\sfF}{\mathsf{F}}
+\DeclareMathOperator{\sfG}{\mathsf{G}}
+\DeclareMathOperator{\sfL}{\mathsf{L}}
+\DeclareMathOperator{\sfP}{\mathsf{P}}
+\DeclareMathOperator{\sfZ}{\mathsf{Z}}
 \DeclareMathOperator{\sgAp}{Ap}
 \DeclareMathOperator{\sgPF}{PF}
+\DeclareMathOperator{\sgehr}{ehr}
 \DeclareMathOperator{\sgconv}{conv}
@@
 \theoremstyle{plain}
-\newtheorem{thm}{Theorem}
-\newtheorem*{thm*}{Theorem}
+\newtheorem{THM}{Theorem}
+\newtheorem*{THM*}{Theorem}
 \newtheorem{lemma}{Lemma}
@@
 \newtheorem*{cor}{Corollary}
-\newtheorem*{prop}{Proposition}
+\newtheorem{prop*}{Proposition}
 \newtheorem*{conj}{Conjecture}
@@
 % Special theorem displays
-\newenvironment{example}%
-	{\begin{leftbar}\begin{example*}
+\newenvironment{thm}%
+  {\begin{leftbar}\begin{THM}
 }{%
-	\end{example*}\end{leftbar}
+  \end{THM}\end{leftbar}
+}
+\newenvironment{thm*}%
+  {\begin{leftbar}\begin{THM*}
+}{%
+  \end{THM*}\end{leftbar}
+}
+\newenvironment{prop}%
+  {\begin{leftbar}\begin{prop*}
+}{%
+  \end{prop*}\end{leftbar}
 }
@@
   \end{definition*}\end{leftbar}
+}
+\newenvironment{example}%
+  {\begin{leftbar}\begin{example*}
+}{%
+  \end{example*}\end{leftbar}
 }
@@
 
-\section*{Prompt:}
+\title{Flow polytopes}
+\author{Nils Olsson}
+\maketitle
+
+Based upon the book \emph{Combinatorial Reciprocity Theorems} by
+Matthias Beck and Raman Sanyal; 2010 \emph{Mathematics Subject Classification}.
+
+\hrulefill
+
+\section*{Topic:}
 
@@
 
-Graphs are a major area of concern in mathematics, having an entire field to
-study dedicated to them. Many different families of graphs exist, but for this
-paper we'll concern ourselves with directed graphs and $\Z_n$-flows on these
-graphs, all concepts which the first section introduces. The second section
-is dedicated to a reciprocity expression for counting the number of possible
-flows on directed graphs, and to developing some insight into it and its proof.
+\section*{Introduction}
+
+Out of all the various topics in mathematics, graph theory is a particularly
+interesting one, and is relevant to a wide variety of other mathematical
+topics as well as computer science.
+What this paper intends to do is, in the first section, is introduce the topic
+of graphs. Many different families of graphs exist, but for this paper we will
+concern ourselves with directed graphs, and $\Z_n$-flow functions which act
+upon these graphs.
+
+Then, in the second section, we will briefly explore the material of
+chapter 7 of Beck and Sanyal's book \emph{Combinatorial Reciprocity Theorems},
+and specifically a single main reciprocity expression theorem:
+\begin{thm*}[Flow counting function]
+  Let $G=(V,E)$ be a graph with a fixed base orientation.
+  Then $\varphi_G(n)$ counts the number of nowhere-zero $\Z_n$-flows of $G$,
+  and is defined:
+  \[
+    \varphi_G(n)
+    =\sum_{\vec b\in\calC(G)}\sgehr_{\sfP_G^\circ(\vec b)}(n)
+    ={(-1)}^{\xi(G)}\sum_{\vec b\in\calC(G)}\sgehr_{\sfP_G(\vec b)}(-n).
+  \]
+\end{thm*}
+What this theorem provides us with is a method of traveling from the topics of
+graphs and combinatorics and into the study of a seemingly unrelated
+mathematical topic: polytopes.
+Specifically, using polytopes to count the number of possible flows
+on directed graphs, subject to a few constraints,
+and even more specifically we will be looking at a way to count only the
+nowhere-zero $\Z_n$-flows of a directed graph.
+This should of course require a brief introduction in polytopes as well,
+but as time permitted this paper wont include an introducting into polytopes or
+Ehrhart reciprocity.
+
+What this paper does \emph{not} intend to do (at least, not anymore) is
+thoroughly explain the proofs of this theorem, in all of its intricacies.
+Instead the second section is a restructuring of parts of chapter 7 in
+Beck and Sanyal's book, in an attempt to provided a clearly progression of
+concepts.
+
+Additionally, this paper will \emph{not} work on a specific example of a graph,
+as I had originally intended. I had hoped to use a very simple directed
+graph to demonstrate some of the underlying mechanics of the propositions and
+theorems of the book, but found it to be beyond my own scope.
+%Instead, we will use a very specific and very simple example of a graph: one
+%with three vertices and an edge between each pair of vertices.
+%Ostensibly this forms a triangle, the simplest type of graph to which this
+%theorem applies to. We will also chose a specific base orientation.
+%It is with this graph that we will develop some intuition into how the main
+%theorem works.
+\begin{figure}[h]
+  \begin{tikzpicture}
+    \path[every node/.style={gdot}]
+      (-1,0) node (v_1){} --
+      ( 1,0) node (v_2){} --
+      ($(0,{sqrt(3)})$) node (v_3){} --
+      cycle;
+    \node[left] at (v_1){$v_1$};
+    \node[right] at (v_2){$v_2$};
+    \node[above] at (v_3){$v_3$};
+    \draw[midarrow] (v_1) -- node (e_1) [below]{$e_1$} (v_2);
+    \draw[midarrow] (v_2) -- node (e_2) [above right]{$e_2$} (v_3);
+    \draw[midarrow] (v_3) -- node (e_3) [above left]{$e_3$} (v_1);
+  \end{tikzpicture}
+  \caption{The intended example graph}
+\end{figure}
 
@@
 
-\section{Introduction to graphs and flows}
+\hrulefill
+
+\section{Graphs and flows}
 
@@
 
-A graph $G=(V,E)$ is a collection of $V$, a set of vertices, and $E$, a set of
-edges between the vertices.
-Now, a graph doesn't have to have any vertices, nor
-does it have to to have any edges (except that if it has edges there must be
-vertices to which those edges connect).
-Also note that the nodes of a graph can be elements of some arbitrary
-d-dimensional space, but for this report we'll only concern ourselves with
-graphs in some two-dimensional space.
-(Note that the word ``node'' is analogous to ``vertex'' and that this paper
-will do plenty of haphazard switching between the two of them.)
+We set off by defining and briefly explaining the topics of both graphs and
+flows.
+A vertex is most intuitively understood as a coordinate in space.
+For instance the coordinates $x=1$ and $y=1$ can define a vertex in
+Euclidean, $\R^2$, space.
+An edges then is a connection between two vertices.
+Edges do not necessarily need to have any particular geometric representation,
+but the concept that two edges can cross over one-another will be required
+later.
+\begin{definition}[Graph]
+  A \emph{graph} $G=(V,E)$ is a collection of $V$, a set of vertices, and $E$, a
+  set of edges between the vertices.
+\end{definition}
+
+Now, a graph does not need to have any vertices.
+In fact a graph with no vertices is still a graph, but it is \emph{the} empty
+graph, and will not be useful in the development of the main theorem.
+Nor does a graph need to have any edges (except that if a graph has edges,
+then there must be vertices to which those edges connect).
+Also, since a graph is just a collection of vertices and edges, we can have
+graphs within graphs, i.e.\ a \emph{subgraph}, which consist of a subset of
+the vertices and edges of the whole graph (in particular, every graph
+necessarily has the empty graph as a subgraph, and every graph has itself as
+a subgraph).
+
+As mentioned before,
+vertices, and by extension a graph, can exist within some arbitrary
+d-dimensional space. However, for this report we will only concern ourselves
+with graphs in two-dimensional, Euclidean space (or at least something
+analogous to two dimensional).
+(I will also point out that the words ``vertex'' and ``node'' are equivalent.
+This paper at times switches between either word, interchangeably.)
+
+So, given a graph with vertices and edges between vertices, we define one
+classification of a subset with at least a few of its vertices, and with
+possibly a few of its edges:
 \begin{definition}[Component, connected component]
   A \emph{connected component} (or simply a \emph{component}) of a graph $G$ is
-  a subgraph (a subset of the vertices and edges of $G$) in which any two
-  vertices are either directly connected via an edge or are connected to
+  a subgraph in which any two
+  vertices are either directly connected via an edge, or are connected to
   one-another via a \emph{path} (a series of vertices and edges). A single
@@
 \end{definition}
+
 Any graph then is the disjoint union of connected components.
@@
   \end{tikzpicture}
-  \caption[Disjoin union]{}
-  \label{fig:disjoint-union}
+  \caption[Disjoin union]{}\label{fig:disjoint-union}
 \end{figure}
+Traversing from one vertex of a graph to another by way of edges only, we see
+that it may be impossible to travel to all of its vertices, hence a graph
+consisting of potentially disjoint components.
 \begin{lemma*}
@@
 \end{definition}
+
 For example, removing the bridge in Figure~\ref{fig:bridge} turns a single
-connected component into two triangular connected components:
+connected component into two disjoint connected components:
 one complete graph into a graph with two complete subgraphs.
@@
       (-.5,.5) node (a) {} ($({-(1+sqrt(3))/2},0)$) node (b) {} ($({-(1+sqrt(3))/2},1)$) node (c) {}
-      ( .5,.5) node (d) {} ($({ (1+sqrt(3))/2},0)$) node (e) {} ($({ (1+sqrt(3))/2},1)$) node (f) {};
+      (.5,.5) node (d) {} ($({ (1+sqrt(3))/2},0)$) node (e) {} ($({ (1+sqrt(3))/2},1)$) node (f) {};
     \draw (a) -- (b) -- (c) -- (a);
@@
   \end{tikzpicture}
-  \caption[Bridges]{A graph with and without a bridge.}
-  \label{fig:bridge}
+  \caption[Bridges]{An undirected graph
+  with and without a bridge.}\label{fig:bridge}
 \end{figure}
@@
   \]
+  The graph $G$ with orientation $\rho$ is denoted ${}_\rho G$.
 \end{definition}
 This definition may be confusing at first glance because $\rho$
-may be missing some of the edges of $E$. What this definition attempts to succinctly
-encapsulate is only the edges with their direction pointing from the vertex of higher
-index to the vertex of lower index (which does certainly feel backwards),
-with all the remaining edges not in $\rho$ directed in the opposite direction,
-from lower to higher index.
-Figure~\ref{fig:directed-graph} tries to illustrate this encapsulation for a graph
-with five vertices and an orientation $\rho=\{14,23,24\}$.
+may be missing some of the edges of $E$. It only includes the edges with
+their direction pointing from the vertex of higher index to the vertex of lower
+index (which does certainly feel backwards).
+Then, all of the edges not in $\rho$ are directed in the opposite
+direction: from lower to higher index.
+
+Figure~\ref{fig:directed-graph} demonstrate how this encapsulation works by
+applying an orientation $\rho=\{14,23,24\}$ onto a particular graph in three
+steps.
 \begin{figure}[ht]
@@
   \end{subfigure}
-  \caption[A directed graph]{A directed graph.}
-  \label{fig:directed-graph}
+  \caption[A directed graph]{A directed graph.}\label{fig:directed-graph}
 \end{figure}
 
-As an aside, directed graphs are the subject of many algorithms in computer
-science, often pertaining to finding optimal ways to traverse the paths of said
-graphs. In some models each edge is considered to be of equal ``weight'' as any
-other. That is if two edges originating from the same node both point to the
-same node, there should be no real preference to traveling down one edge or the
-other to get to the destination. On the other hand we might assign a weight to
+As an aside, there are many algorithms in computer science pertaining to graphs,
+some for finding optimal ways to traverse the paths of graphs. In some
+models each edge is considered to be of equal ``weight'' to any
+other. That is, if two unweighted edges both originate from a node $v_1$
+and both point to a second node $v_2$, then there is no reason to choose one
+edge over the other in traveling from $v_1$ to $v_2$.
+On the other hand, we might assign a weight to
 each edge, presenting a cost-benefit analysis in choosing a path to take (as in
-Figure~\ref{fig:path-finding} where the edge with weight 5 now becomes most
-expensive to traverse versus the one with weight 2).
+Figure~\ref{fig:path-finding}, where the edge with weight 5 now becomes most
+``expensive'' to traverse versus the one with weight 2).
 \begin{figure}[ht]
@@
   \end{tikzpicture}
-  \caption{A directed graph with and without weights.}
-  \label{fig:path-finding}
+  \caption{A directed graph, with and without weights.}\label{fig:path-finding}
 \end{figure}
-Intuitively these weights are often simple $\Z$ integers.
+
+\begin{definition}[Directed path, directed cycle]
+  A \emph{directed path} in ${}_\rho G$ is a sequence $v_0,v_1,\ldots,v_s$ of
+  distinct nodes such that $v_{j-1}\to v_j$ is a directed edge in ${}_\rho G$
+  for all $j=1,\ldots,s$. If $v_s\to v_0$ is also a directed edge, then
+  $v_0,v_1,\ldots,v_s,v_{s+1}=v_0$ is called a \emph{directed cycle}.
+\end{definition}
+
+\begin{definition}[Acyclic orientations]
+  An orientation $\rho$ of $G$ is acyclic if there are no directed cycles in
+  ${}_\rho G$.
+\end{definition}
+
+Dual to the notion of acyclic orientations are orientations which are
+\emph{totally cyclic}, where every edge in ${}_\rho G$ is contained in a
+directed cycle.
+\begin{figure}[h]
+  \begin{tikzpicture}
+    \path[every node/.style={gdot}]
+      (-1, 0) node(a){} --
+      (-1, 1) node(b){} --
+      ( 0, 1) node(c){} --
+      ( 0, 0) node(d){} --
+      ( 1, 0) node(e){} --
+      ( 1, 1) node(f){};
+    \draw[midarrow] (c) -- (d);
+    \draw[midarrow] (a) -- (b);
+    \draw[midarrow] (b) -- (c);
+    \draw[midarrow] (d) -- (a);
+    \draw[midarrow] (e) -- (f);
+    \draw[midarrow] (f) -- (c);
+    \draw[midarrow] (d) -- (e);
+  \end{tikzpicture}
+  \caption{A totally cyclic graph with two cycles.}
+\end{figure}
+
+\begin{definition}[Cyclotomic number]
+  We define the \emph{cyclotomic number} of $G$ as:
+  \[
+    \xi(G)=|E|-|V|+c.
+  \]
+  Where $c=c(G)$ is the number of connected components of $G$.
+\end{definition}
+
+Another topic of graphs is coloring, where every vertex is assigned a color
+value, and a proper coloring is where no vertices connected by an edge share the
+same color. Directions and cycles provide a particular way to induce a coloring
+onto the vertices of a graph, but this is outside the scope of this paper.
+However, acyclic and cyclic orientations are a critical component of
+the main focus of this paper, the nowhere-zero $\Z_n$-flow counting function,
+which we now introduce.
 
@@
 
-Moving on we introduce \emph{flow} values to edges; similar
-values to weights, but living not within $\Z$ but instead within an Abelian
-group $\Z_n=\sfrac\Z n$.
+With a notion of orientations and weights upon the edges of graphs,
+we will now introduce a particular type of weight value that is specific to
+living within an Abelian group $\Z_n=\sfrac\Z n$, and a function which gives
+to every edge of a graph this particular type of weight:
 %(There may also be optimal path algorithms associated
@@
 \begin{definition}[$\Z_n$-flow]
-  A \emph{$\Z_n$-flow} is a map $f:E\to\Z_n$ which to each $e$ edge of $E$
-  assigns a flow ${f(e)\in\Z_n}$ such that there is ``conservation of flow'' at
-  every $v\in V$ vertex, by which me mean the sum of the flows into a vertex $v$
-  is equivalent to the sum of the flows out it:
+  A \emph{$\Z_n$-flow} is a map $f:E\to\Z_n$ which to each edge, $e$, of a
+  directed graph assigns a flow value, ${f(e)\in\Z_n}$, such that there is
+  ``conservation of flow'' at every vertex, $v$, by which me mean the sum of the
+  flows into a vertex is congruent to the sum of the flows out it:
   \[
@@
 \end{definition}
-(And it's important to note equivalence here since $\sum f(e)\in\Z_n$.)
-These functions and more specifically counting them will be the ultimate
-purpose of this paper.
+
+It is these flow functions that are the subject of the main theorem of this
+paper, in particular counting how many different flows can be constructed for
+a particular directed graph given the constraint of conservation.
+It is especially important to note that because the flow values are elements of
+an Abelian group $\Z_n$ that there is necessarily a finite number of flow
+functions that can be applied to any particular graph since each flow value
+has to be one of $n$ possible values, modulus $n$.
+
 \begin{definition}[$f$ support]
@@
 Figure~\ref{fig:graph-flows} illustrates two different but satisfactory
-$\Z_5$-flows on a graph. Without the context of the Abelian group $Z_5$
-these flows wouldn't seem to work, but, since $3+2\equiv 0\bmod 5$,
-the top and bottom left vertices both have conservation of flow
-equal to zero.
+$\Z_5$-flows on a graph.
+As simple integer weights, the second flow would not fullfil the conservation
+requirement, since from vertex $v_1$ we have in input of 0 and an output of
+$2+3=5$,
+but as elements of the Abelian group $Z_5$ they work, since
+$5\equiv 0\bmod 5$.
 \begin{figure}[ht]
@@
     \path
-      (0,1) node (a)[gdot]{}
-      ($({cos(  -pi/6 r)},{sin(  -pi/6 r)})$) node (b)[gdot]{}
-      ($({cos(-5*pi/6 r)},{sin(-5*pi/6 r)})$) node (c)[gdot]{};
+      (0,1) node (a)[gdot,label=$v_1$]{}
+      ($({cos(  -pi/6 r)},{sin(  -pi/6 r)})$) node (b)[gdot,label=right:$v_2$]{}
+      ($({cos(-5*pi/6 r)},{sin(-5*pi/6 r)})$) node (c)[gdot,label=left:$v_3$]{};
     \draw[midarrow] (a) -- node[right]{0} (b);
@@
     \path
-      (0,1) node (a)[gdot]{}
-      ($({cos(  -pi/6 r)},{sin(  -pi/6 r)})$) node (b)[gdot]{}
-      ($({cos(-5*pi/6 r)},{sin(-5*pi/6 r)})$) node (c)[gdot]{};
+      (0,1) node (a)[gdot,label=$v_1$]{}
+      ($({cos(  -pi/6 r)},{sin(  -pi/6 r)})$) node (b)[gdot,label=right:$v_2$]{}
+      ($({cos(-5*pi/6 r)},{sin(-5*pi/6 r)})$) node (c)[gdot,label=left:$v_3$]{};
     \draw[midarrow] (a) -- node[right]{2} (b);
@@
   \end{tikzpicture}
-  \caption{An everywhere-zero $\Z_5$-flow and a nowhere-zero $\Z_5$-flow.}
-  \label{fig:graph-flows}
+  \caption{An everywhere-zero $\Z_5$-flow and a nowhere-zero $\Z_5$-flow.}\label{fig:graph-flows}
 \end{figure}
 
-Going forward, $G$ will always refer to a 2-dimensional graph with $V$ vertices
-and $E$ edges, $\rho$ to an arbitrary (but fixed) orientation of $G$
-and $\Z_n$ to an Abelian group to which $f$ a $\Z_n$-flow maps.
-\begin{definition}
+%Going forward, $G$ will always refer to a 2-dimensional graph with $V$ vertices
+%and $E$ edges, $\rho$ to an arbitrary  orientation of $G$
+%and $\Z_n$ to an Abelian group to which $f$ a $\Z_n$-flow maps.
+And now we introduce the main focus of this paper.
+\begin{definition}[Nowhere-zero $\Z_n$-flow counting function]
   Define a counting function:
@@
 \end{prop}
-(The proof of this is a ``left to the reader'' exercise in the original paper.)
 \begin{prop}
@@
   %\end{subfigure}
-  \caption{Various graphs and their duals.}
-  \label{fig:graphs-and-duals}
+  \caption{Various graphs and their duals.}\label{fig:graphs-and-duals}
 \end{figure}
@@
 % ------------------------------------------------------------------------------
-\pagebreak
-\section{Reciprocity in counting graph flows}
+\hrulefill
 
-Ultimately the purpose of this report is in providing some intuition into the
-following theorem and its proof:
-\begin{thm}\label{thm:1.2.5}
-  Let $G$ be a bridgeless graph. For every positive integer $n$, the
-  reciprocity statement:
+\section{Reciprocity in counting nowhere-zero $\Z_n$-flows}
+
+Originally my intention of this second section of the paper was to demonstrate,
+by example, the underlying mechanisms of the theorems and propositions in the
+Beck and Sanyal book. Instead what I found was that my grasp on the topic was
+shaky at best. What proved the most useful, to me at least, was to piece
+together a different order of the book's chapter 7 definitions, propositions and
+theorems; an order which feels much more natural in moving from a graph and
+combinatorial centric topic of flows, into a more polytope centric topic of
+reciprocity expressions.
+It was also at this time that I recognized that many topic introduced in the
+first second of this paper would now have no connection to this second section,
+specifically dual graphs and cyclic/acyclic orientations.
+They are in fact critical in the proofs of the propositions behind the
+$\Z_n$-flow counting function, but by limitations of time wont find any use
+here-on-out.
+
+%Instead of regurgitate the general proof of the main theorem, in this section we
+%will observe the mechanics of the theorem by studying a specific directed graph
+%with vertices $V=\{v_1,v_2,v_3\}$,
+%edges $E=\{e_1=v_1v_2,e_2=v_2v_3,e_3=v_3v_1\}$, and
+%base orientation $\rho=\{21,32,31\}$.
+%\begin{figure}[h]
+  %\begin{tikzpicture}
+    %\path[every node/.style={gdot}]
+      %(-1,0) node (v_1){} --
+      %( 1,0) node (v_2){} --
+      %($(0,{sqrt(3)})$) node (v_3){} --
+      %cycle;
+    %\node[left] at (v_1){$v_1$};
+    %\node[right] at (v_2){$v_2$};
+    %\node[above] at (v_3){$v_3$};
+    %\draw[midarrow] (v_1) -- node (e_1) [below]{$e_1$} (v_2);
+    %\draw[midarrow] (v_2) -- node (e_2) [above right]{$e_2$} (v_3);
+    %\draw[midarrow] (v_3) -- node (e_3) [above left]{$e_3$} (v_1);
+  %\end{tikzpicture}
+  %\caption{Our graph, $G=(V,E)$.}\label{fig:our_graph}
+%\end{figure}
+%We choose this graph in particular for its simplicity. It is (I believe) the
+%simplest example of a bridgeless, connected, and totally cyclic graph.
+
+We begin by recalling that flows are functions which assign to every edge of a
+directed graph a value such that there is conservation of flow at every vertex:
 \[
-    {(-1)}^{\xi(G)}\varphi_G(-n)
+  \sum_{u\rightarrow v}f(uv)-\sum_{u\leftarrow v}f(uv)=0.
 \]
-  counts the number of pairs $(f,p)$,
-  where $f$ is a $\Z_n$-flow and $\rho$ is a totally-cyclic reorientation of
-  $G/\sgsupp(f)$. In particular, when $n=-1$, the statement equals the
-  number of totally-cyclic orientations of $G$.
-\end{thm}
+What may not be obvious from the presentation of this equation is that it is
+specific to the vertex $v$ and not to $u$. Rather, $u$ pertains to the other
+side of an edge, pointing towards $v$ or away from it; there may be many
+different $u$ vertices, depending on how many edges connect to a particular $v$.
 
-Going forward we'll attempt to build some insight into theorem~\ref{thm:1.2.5}
-and its proof, and into the propositions upon which the proof relies.
+We will also pay attention to the specific order of the vertices in $V$ and the
+specific order of the edges in $E$.
+What this provides us with is a way to think of flow functions as coordinates,
+where each flow value is a component of a $m$-dimensional coordinate,
+indexed by the edge onto which it is assigned:
+\[
+  f=(f(e_1),f(e_2),\ldots,f(e_m)).
+\]
+This is extremely important, as it allows us to eventually build polytopes
+from collections of possible flows.
 
-\subsection{Flows and flow spaces}
+%(Note that the source paper introduces flows as being real-valued, but I will
+%gloss over this as it is real-valued flows are really only necessary in the
+%proof of various propositions.)
 
-As a matter of notation, for a vertex $v$, $uv$ is a directed edge pointing
-either from a vertex $u$ towards $v$, or from $v$ to $u$. Now to slightly mangle
-a previous definition, we now define flows, as opposed to $Z_n$-flows:
-\begin{definition}[Flow]
-  For $G=(V,E)$ a graph and $\Z_n$ an Abelian group, we define a
-  \emph{nowhere-zero flow}, $f:E\to\Z$, to be a map such that $0<f(e)<n$ for all
-  $e\in E$, and which for all $v\in V$ with an integer $b_v$ (corresponding to
-  $v$) satisfies the equation:
+Also recall that $\Z_n$-flows (a specific kind of flow function)
+assign to edges flow values which are elements of an Abelian group $\Z_n$.
+The conservation equation then is modified to look more like the remainder
+algorithm:
+\begin{equation}
+  \sum_{u\rightarrow v}f(uv)-\sum_{u\leftarrow v}f(uv)=nb_v.\label{eqn:flow_conservation}
+\end{equation}
+Where $b_v$ is an integer, and each $b_v$ corresponds to a specific vertex $v$
+of our graph. That is, $b_1$ corresponds to $v_1$, $b_2$ to $v_2$,
+and $b_3$ to $v_3$.
+We will collect these $b_v$ values into a vector $\vec b=(b_1,b_2,b_3)\in \Z^V$
+in order of the vertices,
+just as we considered the order of the edges in calling a flow $f$ a
+coordinate.
+
+We should note that the $\Z_n$-flows, $f\in\Z_n^E$, are just one particular
+solution to this inequality (it's actually surprising to me that the book never
+uses the notation $\Z_n^E$ for flow values corresponding to the vertices). Many
+more solutions may exist, in particular for real-valued flows, $f\in\R^E$.
+Certainly it is confusing having the symbol $f$ change family like this, and the
+book makes little-to-no distinction.
+%
+Even so, for $\vec b\in\Z^V$ we define the following:
+\begin{definition}[Subspace of flows]
+  Let $G=(V,E)$ be a graph with a fixed base orientation.
+  We define $\calF(\vec b)\subseteq\R^E$ to be the
+  affine subspace of all $f\in\R^E$ real-valued flows
+  (also considering $f$ as a real-valued coordinate)
+  satisfying~\eqref{eqn:flow_conservation} when $n=1$.
+\end{definition}
+
+Moving towards our goal, the number of nowhere-zero $\Z_n$-flows of $G$,
+$\varphi_G(n)$, then (hinting to polytopes) is the number of lattice points in
 \[
-    \sum_{u\to v}f(uv)-\sum_{v\to u}f(uv)=nb_v.
+  n{(0,1)}^E\cap\bigcup_{\vec b\in\Z^V}\calF_G(n\vec b).
+\]
+However this collection contains much more than just the lattice points,
+since $\calF_G(n\vec b)$ contains all real-valued flows.
+
+Another important property of the flow subspaces to note is when
+$\vec b=\vec 0$. In fact we give this particular subspace its own definition:
+\begin{definition}[Flow space]
+  Let $G=(V,E)$ be a graph with a fixed base orientation.
+  We call $\calF_G(\vec 0)$ the \emph{flow space} of $G$, and simply
+  denote it $\calF_G$.
+\end{definition}
+Notice that, for the flow space, equation~\eqref{eqn:flow_conservation} turns
+into an inequality:
+\[
+  \sum_{u\rightarrow v}f(uv)=\sum_{u\leftarrow v}f(uv).
+\] 
+This condition is called the \emph{conservation of flow} at every $v$,
+hearkening back to the original definition of weights and flows, in the first
+section of this paper.
+An important takeaway from this fact is that for any $\vec b\in\Z^E$,
+$\calF_G(\vec b)=t+\calF_G(\vec 0)$
+for some $t\in\R^E$, meaning that the dimension of the flow subspace
+$\calF_G(\vec b)$ (not to be confused with the flow space $\calF$)
+is actually independent of $\vec b$.
+As I wont be including any of the proofs of the book in the paper, the following
+proposition may not be obvious.
+\begin{prop}
+  Let $G=(V,E)$ be a graph with a fixed base orientation.
+  Then the dimension of the flow space $\dim\calF_G=\xi(G)$.
+\end{prop}
+But what this proposition hints at is the relation between cycles in a graph
+and the flow space (recall that $\xi(G)$ is the cyclotomic number of a graph
+$G$).
+
+Going back to the $\vec b$ vectors,
+we make the following set definition by recognizing that although many of the
+$\vec b$ vectors may satisfy equation~\eqref{eqn:flow_conservation}, many
+still may be somewhere-zero flows:
+\begin{definition}[Nowhere-zero flow vectors]
+  Let $\calC(G)\subset\Z^V$ be the set of all $\vec b$ vectors such that:
+  \[
+    {(0,1)}^E\cap\calF_G(\vec b)\ne\emptyset.
   \] 
 \end{definition}
-This should appear very similar to the conservation equation in the
-definition of $\Z_n$-flow functions,
-but the distinction is that $\Z_n$-flows map to $\Z_n$ and flows map to $\Z$.
-Nevertheless, since the difference of the sums in the equation of the definition
-above is equal to a multiple of $n$, the sums are indeed congruent modulo $n$,
-similar to the conservation in the definition of $\Z_n$-flows.
-(I'll present the justification for this distinction between $\Z_n$-flows and
-flows soon.)
+The book makes no name for this set, but we will refer to it as the nowhere-zero
+flow vector set.
 
-Next we introduce a specific space of these function
-(as well as further mangle the definition of the $f$ flow ``functions''!):
-\begin{definition}
-  For $\vec b\in\Z^V$ a vector, we define $\calF_G(\vec b)\subseteq\R^E$ to be
-  the affine subspace of all $f\in\R^E$ satisfying the equation of the previous
-  definition but specifically for $n=1$.
-\end{definition}
-What I meant by further mangle is that now we don't consider $f$ only as
-a function, but now also as a coordinate in $\R^E$ space.
-What is $\R^E$ space you ask?
-It is ${\lvert E\rvert}$-dimensional, but we don't call it $\Z^{\lvert E\rvert}$
-space because: each component of a coordinate is indexed by the edges themselves
-as opposed to a more familiar scheme such as $x_1,x_2,x_3,\ldots$.
+\hrulefill
 
-I certainly had a hard time processing this dual representation, so I'll
-attempt to give a brief example to explain this relationship from function to
-coordinate:
-\begin{example}
-  Fix $G$ a directed graph with four edges, $E=\{e_a,e_b,e_c,e_d\}$,
-  and $f\in\Z^E$ a nowhere-zero flow on $G$ for some Abelian group $\Z_n$.
-  Suppose $f$, being a coordinate in $\Z^E$ space,
-  is the coordinate $(4,2,7,5)$ which maps the edges of the graph in the order
-  as they appear above.
-  Here then is a sort of condensing of $f$'s various representation:
+Finally we are ready move into the world of polytopes proper.
+In particular we can start to see
+that the polytope we are constructing
+will have vertices corresponding to the flows of $G$.
+Thus we also define:
+\begin{definition}[Flow polytope]
   \[
-    f=(4,2,7,5)\in\Z^4,~f(e)\in\{4,2,7,5\}
-  \]
-	And then the action of mapping:
-  \[
-    f(e_a)=4,~f(e_b)=2,~f(e_c)=7,~f(e_d)=5
-  \]
-\end{example}
-But what prompts/justifies this mangling of definitions?
-Well, what is ultimately being sought after is a way to relate $\Z_n$-flow
-functions to lattice points in/on some polytope, and vice versa:
-%
-flows $f$ which are points in $n{(0,1)}^E\cap \Z^E$.
-(Note that $n{(0,1)}^E$ is the n'th dilation of all real-valued points contained
-within the ${\lvert E\rvert}$-dimensional open unit cube---no points on the
-boundaries. Then the intersection with $\Z^E$ yields only those points that are
-lattice/integer point.)
-
-\begin{definition}[Flow space]
-  $\calF_G(\vec 0)$ is the \emph{flow space} of $G$ such that each $f$
-  satisfies the conservation equation:
-  \[
-    \sum_{u\to v}f(uv)=\sum_{v\to u}f(uv).
+    \sfP_G(\vec b)={[0,1]}^E\cap\calF_G(\vec b).
   \]
 \end{definition}
-This should now look very familiar to $Z_n$-flows, which from the get-go were
-defined with conservation of flow.
+As an intersection of half-spaces and hyperplanes, $\sfP_G(\vec b)$ is indeed a
+polytope, and note that since $\sfP_G(\vec b)\subseteq{[0,1]}^E$, the lattice
+points of $\sfP_G(\vec b)$ are exactly its vertices.
+\begin{prop}
+  Let $G=(V,E)$ be a graph with a fixed base orientation.
+  Then $\sfP_G(\vec b)$ is a lattice polytope for every $\vec b\in\Z^V$.
+\end{prop}
 
-(And eventually I get to actually talking about theorem~\ref{thm:1.2.5}!)
+By dilating this polytope by a factor $n$ corresponding to the
+Abelian group $\Z_n$, $n\sfP_G(\vec b)$ represents the number of
+$\Z_n$-flows on $G$, and in particular the nowhere-zero $\Z_n$-flows 
+correspond to the lattice points laying within the interior of this polytope.
+Also note that when $n=1$, this polytope \emph{has no}
+nowhere-zero $\Z_n$-flows (specifically $\Z_1$-flows) since no lattice points
+sit within the unit cube ${[0,1]}^E$. Only when $n\ge 2$ will nowhere-zero
+$\Z_n$-flows exist.
+
+Then finally we reach our goal of a reciprocity expression:
+\begin{thm}[Flow counting function]
+  Let $G=(V,E)$ be a graph with a fixed base orientation.
+  Then $\varphi_G(n)$ counts the number of nowhere-zero $\Z_n$-flows of $G$,
+  and is defined:
+  \[
+    \varphi_G(n)
+    =\sum_{\vec b\in\calC(G)}\sgehr_{\sfP_G^\circ(\vec b)}(n)
+    ={(-1)}^{\xi(G)}\sum_{\vec b\in\calC(G)}\sgehr_{\sfP_G(\vec b)}(-n).
+  \]
+\end{thm}
+Beck and Sanyal don't state this definition as it's own theorem but I think it's
+worthy of being called a theorem, especially with respect to the main topic of
+their book: combinatorial reciprocity theorems.
+
+\hrulefill
+
+\section*{Conclusion and farewell}
+
+Ultimately, I end the paper with the statement of this function, as time
+has become the most limiting factor. To fully appreciate this last theorem
+requires an full reintroduction polytopes and Ehrhart reciprocity (especially
+since without this we don't exactly have a way to even calculate
+the $\sgehr_{\sfP_G(\vec b)}(-n)$ expression!).
+But hopefully what we are able to take away is the ability of polytopes to
+act as a bridge between seemingly unrelated fields of mathematics.
+
+At many times, this reading project has been an absolute blast, and at others
+has been an absolute slog of feeling lost and confused. But this last draft
+does have be recommitted to the understanding that I can in-fact grasp these
+topics, given enough time and energy, and hopefully by developing my own
+structure of chapter 7 of Beck and Sanyal's book I will be able to come back to
+this in the future and have an easier time getting caught up, instead of getting
+lost in what I thought was an organization mess in the original.
+
+Cheers!
+
+%Lets apply a $\Z_5$-flow to our graph: $f:(e_1,e_2,e_3)\to(1,1,1)$.
+%\begin{figure}[h]
+  %\begin{tikzpicture}
+    %\path[every node/.style={gdot}]
+      %(-1,0) node (v_1){} --
+      %( 1,0) node (v_2){} --
+      %($(0,{sqrt(3)})$) node (v_3){} --
+      %cycle;
+    %\node[left] at (v_1){$v_1$};
+    %\node[right] at (v_2){$v_2$};
+    %\node[above] at (v_3){$v_3$};
+    %\draw[midarrow] (v_1) -- node (e_1) [below]{$f(e_1)=1$} (v_2);
+    %\draw[midarrow] (v_2) -- node (e_2) [above right]{$f(e_2)=1$} (v_3);
+    %\draw[midarrow] (v_3) -- node (e_3) [above left]{$f(e_3)=1$} (v_1);
+  %\end{tikzpicture}
+%\end{figure}
+%It is trivial enough to see that this is a valid flow.
+
+%If we could evaluate this expression for our graph now, we would have:
+%\begin{gather*}
+  %\intertext{(The number of connected components:)}
+  %c=1 \\
+  %\intertext{(The cyclical number:)}
+  %\xi(G)=3-3+1=1 \\
+  %\intertext{(And so:)}
+  %{(-1)}^{1}\varphi_G(-5)=?
+%\end{gather*}
+
+%\hrulefill
+
+%Similarly, the number of nowhere-zero $\Z_n$-flows of $G$ are
+
+%(Old:)
+
+%Ultimately the purpose of this report is in providing some intuition into the
+%following theorem and its proof:
+%\begin{thm}\label{thm:1.2.5}
+  %Let $G$ be a bridgeless graph. For every positive integer $n$, the
+  %reciprocity statement:
+  %\[
+    %{(-1)}^{\xi(G)}\varphi_G(-n)
+  %\]
+  %counts the number of pairs $(f,p)$,
+  %where $f$ is a $\Z_n$-flow and $\rho$ is a totally-cyclic reorientation of
+  %$G/\sgsupp(f)$. In particular, when $n=-1$, the statement equals the
+  %number of totally-cyclic orientations of $G$.
+%\end{thm}
+
+%Going forward we'll attempt to build some insight into Theorem~\ref{thm:1.2.5}
+%and its proof, and into the propositions upon which the proof relies.
+
+%\subsection{Flows and flow spaces}
+
+%As a matter of notation, for a vertex $v$, $uv$ is a directed edge pointing
+%either from a vertex $u$ towards $v$, or from $v$ to $u$. Now to slightly mangle
+%a previous definition, we now define flows, as opposed to $Z_n$-flows:
+%\begin{definition}[Flow]
+  %For $G=(V,E)$ a graph and $\Z_n$ an Abelian group, we define a
+  %\emph{nowhere-zero flow}, $f:E\to\Z$, to be a map such that $0<f(e)<n$ for all
+  %$e\in E$, and which for all $v\in V$ with an integer $b_v$ (corresponding to
+  %$v$) satisfies the equation:
+  %\[
+    %\sum_{u\to v}f(uv)-\sum_{v\to u}f(uv)=nb_v.
+  %\]
+%\end{definition}
+%This should appear very similar to the conservation equation in the
+%definition of $\Z_n$-flow functions,
+%but the distinction is that $\Z_n$-flows map to $\Z_n$ and flows map to $\Z$.
+%Nevertheless, since the difference of the sums in the equation of the definition
+%above is equal to a multiple of $n$, the sums are indeed congruent modulo $n$,
+%similar to the conservation in the definition of $\Z_n$-flows.
+%(I'll present the justification for this distinction between $\Z_n$-flows and
+%flows soon.)
+
+%Next we introduce a specific space of these function
+%(as well as further mangle the definition of the $f$ flow ``functions''!):
+%\begin{definition}
+  %For $\vec b\in\Z^V$ a vector, we define $\calF_G(\vec b)\subseteq\R^E$ to be
+  %the affine subspace of all $f\in\R^E$ satisfying the equation of the previous
+  %definition but specifically for $n=1$.
+%\end{definition}
+%What I meant by further mangle is that now we don't consider $f$ only as
+%a function, but now also as a coordinate in $\R^E$ space.
+%What is $\R^E$ space you ask?
+%It is ${\lvert E\rvert}$-dimensional, but we don't call it $\Z^{\lvert E\rvert}$
+%space because: each component of a coordinate is indexed by the edges themselves
+%as opposed to a more familiar scheme such as $x_1,x_2,x_3,\ldots$.
+
+%I certainly had a hard time processing this dual representation, so I'll
+%attempt to give a brief example to explain this relationship from function to
+%coordinate:
+%\begin{example}
+  %Fix $G$ a directed graph with four edges, $E=\{e_a,e_b,e_c,e_d\}$,
+  %and $f\in\Z^E$ a nowhere-zero flow on $G$ for some Abelian group $\Z_n$.
+  %Suppose $f$, being a coordinate in $\Z^E$ space,
+  %is the coordinate $(4,2,7,5)$ which maps the edges of the graph in the order
+  %as they appear above.
+  %Here then is a sort of condensing of $f$'s various representation:
+  %\[
+    %f=(4,2,7,5)\in\Z^4,~f(e)\in\{4,2,7,5\}
+  %\]
+  %And then the action of mapping:
+  %\[
+    %f(e_a)=4,~f(e_b)=2,~f(e_c)=7,~f(e_d)=5
+  %\]
+%\end{example}
+%But what prompts/justifies this mangling of definitions?
+%Well, what is ultimately being sought after is a way to relate $\Z_n$-flow
+%functions to lattice points in/on some polytope, and vice versa:
+
+%flows $f$ which are points in $n{(0,1)}^E\cap \Z^E$.
+%(Note that $n{(0,1)}^E$ is the n'th dilation of all real-valued points contained
+%within the ${\lvert E\rvert}$-dimensional open unit cube---no points on the
+%boundaries. Then the intersection with $\Z^E$ yields only those points that are
+%lattice/integer point.)
+
+%\begin{definition}[Flow space]
+  %$\calF_G(\vec 0)$ is the \emph{flow space} of $G$ such that each $f$
+  %satisfies the conservation equation:
+  %\[
+    %\sum_{u\to v}f(uv)=\sum_{v\to u}f(uv).
+  %\]
+%\end{definition}
+%This should now look very familiar to $Z_n$-flows, which from the get-go were
+%defined with conservation of flow.
+
+%(And eventually I get to actually talking about Theorem~\ref{thm:1.2.5}!)
 
